### 2019-02-25 code/paper.Rmd
code dir

---
title: "Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia"
---

What countries are most represented?

```{r}
library("rnaturalearth")
library("rnaturalearthdata")
world <- ne_countries(scale = "medium", returnclass = "sf")

  # get country of site from location text
  # Laos, Czech Republic, Micronesia, Zimbabwe, South Sudan, Chad, 
  # Central African Republic, Congo, Gabon, Cameroon, Nigeria, Bosnia and Herzegovina
  #  Cote d'Ivoire, Sierra Leone, Guyana, Belize, 
  country_names <-  paste(c(world$name, 
                            "United States",
                            "Czech Republic",
                             "Antigua & Barbuda",
                            "Saint Kitts and Nevis"
                            ),
                          collapse="|")

  page_data_for_all_pages_location <- 
    page_data_for_all_pages %>% 
    mutate(country = str_extract(Location, 
                                 regex(country_names, 
                                       ignore.case=TRUE))) %>% 
    mutate(country = case_when(
      country == "United States" ~ "United States of America",
      country == "Czech Republic" ~ "Czechia",
      country == "Antigua & Barbuda" ~ "Antigua and Barb.",
      country == "Saint Kitts and Nevis" ~ "St. Kitts and Nevis",
      TRUE ~ as.character(country)))

wh_wk_country_counts <- 
page_data_for_all_pages_location %>% 
  count(country) %>% 
  filter(!is.na(country))

theme_nogrid <- function (base_size = 12, base_family = "") {
  theme_bw(base_size = base_size, 
           base_family = base_family) %+replace% 
    theme(panel.grid = element_blank() )   
}

wh_wk_country_counts_hist <- 
ggplot(wh_wk_country_counts,
       aes(n)) +
  geom_histogram() +
  theme_nogrid(14)

wh_wk_country_counts_bar <- 
ggplot(wh_wk_country_counts,
       aes(reorder(country, n),
           n)) +
  geom_col() +
  coord_flip() +
  theme_minimal(base_size = 6) +
  xlab("")
```

Here's a map of countries showing which has the most WP pages for WH sites

```{r}
sf_map_data <- 
world %>% 
  filter(name != "Antartica") %>% 
  left_join(wh_wk_country_counts,
            by = c( 'name' = 'country')) %>% 
  select(name, n, geometry)

wh_wk_country_count_map <- 
ggplot(data = sf_map_data) +
    geom_sf(aes(fill = n)) +
    scale_fill_viridis_c(na.value="grey90") +
  coord_sf() +
  theme_minimal()
```

Combine map and histogram

```{r}
wh_wk_country_count_map +
  annotation_custom(ggplotGrob(wh_wk_country_counts_hist), 
                    xmin = -190, 
                    xmax = -90, 
                    ymin= 10, 
                    ymax=-70) 
```

Map of the ratio of WH sites with WP pages, per country

```{r}

```

  - length of articles http://citeseerx.ist.psu.edu/viewdoc/download?doi=10.1.1.451.4208&rep=rep1&type=pdf 
  - edit history to identify: diversity of contributions, 
  - reverts in edits for spotting contentious topics https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0038869 http://www.contropedia.net/  http://wwm.phy.bme.hu/ 
    - vandalism traces in edit history
  - talk page length
  - number of links in each page
  - page views: https://www.sciencedirect.com/science/article/abs/pii/S0006320716301240 
  - timing of edits: political events? Brexit?
    - citations in articles: https://arxiv.org/abs/0705.2106
  - are the citations scholarly? Archaeological? Meskell?
    - citations to these articles: https://www.tandfonline.com/doi/full/10.1080/0194262X.2016.1206052 
  - network analysis of editors, clusters of editors
  - sentiment analysis of talk pages
  - geolocation of anon editors by IP address
  - bots and technicity https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0171774 but see https://dl.acm.org/citation.cfm?id=3134684

  - Compare to 10000 random Wikipedia sites
  - Compare to WH sites in media & academic literature

### 2019-02-25 001-EDA.R

@@ -1,181 +1,0 @@
-names(page_data_for_all_pages$result)
-
-#--------------------------------------------------------------------------
-# take a look at the distribution of page variables
-some_page_variables <- 
-  page_data_for_all_pages$result %>% 
-  select(page_wordcount, 
-         page_wikilinks_out,
-         page_wikilinks_in,
-         page_cited_items_on) %>% 
-  mutate(page_wikilinks_out_norm = page_wikilinks_out / page_wordcount,
-         page_cited_items_on_norm = page_cited_items_on / page_wordcount) 
-  
-some_page_variables %>% 
-  gather(variable, value) %>% 
-ggplot(aes(value)) +
-  geom_histogram() +
-  facet_wrap( ~ variable, 
-              scales = "free") +
-  scale_x_log10() +
-  theme_minimal()
-
-library(GGally)
-ggpairs( some_page_variables %>% 
-           mutate_all(log)) +
-  theme_minimal()
-
-# umap
-library(uwot)
-pages_umap_input <- 
-  some_page_variables  %>% 
-  mutate(page_wordcount_scaled = scale(page_wordcount),
-         page_wikilinks_in_scaled = scale(page_wikilinks_in)) %>% 
-  select(-page_wordcount,
-         -page_cited_items_on, 
-         -page_wikilinks_out,
-         -page_wikilinks_in) %>% 
-  bind_cols(., page_data_for_all_pages$result[ , 'country'] ) %>% 
-  filter_all(all_vars(!is.na(.))) %>% 
-  left_join(World %>% 
-              select(name, continent), 
-            by = c('country' = 'name'))
-
-# compute umap
-
-pages_umap_input_selected <- 
-  pages_umap_input %>% 
-  select(-country, 
-         -continent,
-         -geometry
-         )  
-    
-pages_umap_output <- 
-  pages_umap_input_selected %>% 
-  umap(., 
-       n_neighbors = 50, 
-       min_dist = 0.9,
-       nn_method = "annoy",
-       init = "spca") %>% 
-  as_tibble()
-
-# compute hdbscan clusters
-library(dbscan)
-hdbscan_out <- hdbscan(pages_umap_output, 
-                       minPts = 5)
-
-table(hdbscan_out$cluster)
-
-main_plot <- 
-ggplot(pages_umap_output,
-       aes(V1, V2)) +
-  geom_point(size = 3,
-             aes(colour = factor(hdbscan_out$cluster))) +
-  scale_color_viridis_d(guide = FALSE) +
[…]

### 2019-02-25 code/000-scrape-wikipedia-random-pages.R

@@ -5,8 +5,8 @@ library(vegan)
 # gets a random WP page
 rando <- "https://en.wikipedia.org/wiki/Special:Random"
 
-# gets data about 1000 WP pages
-n <- 10
+# gets data about n WP pages
+n <- 10000
 random_page_data <- rerun(n, get_data_about_page_safe(rando) )
 
 # drops the pages that returned an error

### 2019-02-25 code/001-EDA.R

@@ -1,0 +1,306 @@
+library(tidyverse)
+
+page_data_for_all_pages <- readRDS("data/page_data_for_all_pages.rds")
+
+names(page_data_for_all_pages)
+
+normalize = function(x) (x-min(x))/(max(x)-min(x))
+
+#--------------------------------------------------------------------------
+# take a look at the distribution of page variables
+some_page_variables <- 
+  page_data_for_all_pages %>% 
+  select(page_wordcount, 
+         page_wikilinks_out,
+         page_wikilinks_in,
+         page_cited_items_on) %>% 
+  mutate(page_wikilinks_out_per_word = page_wikilinks_out / page_wordcount,
+         page_cited_items_on_per_word = page_cited_items_on / page_wordcount) 
+  
+some_page_variables %>% 
+  gather(variable, value) %>% 
+ggplot(aes(value)) +
+  geom_histogram() +
+  facet_wrap( ~ variable, 
+              scales = "free") +
+  scale_x_log10() +
+  theme_minimal()
+
+library(GGally)
+ggpairs( some_page_variables %>% 
+           mutate_all(log)) +
+  theme_minimal()
+
+# umap
+library(uwot)
+library("tmap")
+data("World")
+
+pages_umap_input <- 
+  some_page_variables  %>% 
+  mutate(page_wordcount_norm = normalize(page_wordcount),
+         page_wikilinks_in_norm= normalize(page_wikilinks_in),
+         page_wikilinks_out_per_word_norm = normalize(page_wikilinks_out_per_word),
+         page_cited_items_on_per_word_norm = normalize(page_cited_items_on_per_word)) %>% 
+  select(-page_wordcount,
+         -page_cited_items_on, 
+         -page_wikilinks_out,
+         -page_wikilinks_in,
+         -page_wikilinks_out_per_word,
+         -page_cited_items_on_per_word) %>% 
+  bind_cols(., page_data_for_all_pages[ , 'country'] ) %>% 
+  filter_all(all_vars(!is.na(.))) %>% 
+  left_join(World %>% 
+              select(name, continent), 
+            by = c('country' = 'name'))
+
+# compute umap
+
+pages_umap_input_selected <- 
+  pages_umap_input %>% 
+  select(-country, 
+         -continent,
+         -geometry
+         )  
+    
+pages_umap_output <- 
+  pages_umap_input_selected %>% 
[…]

### 2019-02-25 code/paper.Rmd
maps

@@
 ---
+
+Load the data
+
+```{r}
+library(tidyverse)
+
+# all WH sites with WP pages (n = 584)
+page_data_for_all_pages <- readRDS("data/page_data_for_all_pages.rds")
+
+# all WH sites, with and without WP pages (n = 846)
+wh_wiki_table <- read_csv('data/wh_wiki_table.csv')
+
+```
 
@@
 
+wh_wiki_table_location <- 
+  wh_wiki_table %>% 
+  mutate(country = str_extract(Location, 
+                                 regex(country_names, 
+                                       ignore.case=TRUE))) %>% 
+    mutate(country = case_when(
+      country == "United States" ~ "United States of America",
+      country == "Czech Republic" ~ "Czechia",
+      country == "Antigua & Barbuda" ~ "Antigua and Barb.",
+      country == "Saint Kitts and Nevis" ~ "St. Kitts and Nevis",
+      TRUE ~ as.character(country)))
+
+```
+
+```{r}
+
 wh_wk_country_counts <- 
@@
 
+median_number_wp_pages_per_country <- 
+  median(wh_wk_country_counts$n)
+
+estimate_mode <- function(x) {
+  d <- density(x)
+  d$x[which.max(d$y)]
+}
+
+mode_number_wp_pages_per_country <- 
+  round(estimate_mode(wh_wk_country_counts$n), 1)
+
 wh_wk_country_counts_hist <- 
@@
   geom_histogram() +
-  theme_nogrid(14)
+  annotate("text", x = 15, y = 30, 
+           label = str_glue('Median = {median_number_wp_pages_per_country} WP pages/country\nMode = {mode_number_wp_pages_per_country} WP pages/country'),
+           size = 2) +
+  theme_nogrid(12)
 
@@
 ```{r}
+wh_wiki_table_location_prop <- 
+wh_wiki_table_location %>% 
+  mutate(has_wp_page = ifelse(!is.na(site_page_name), 1, 0)) %>% 
+  group_by(country) %>% 
+  summarise(prop_sites_with_pages = sum(has_wp_page) / n()) %>% 
+  filter(!is.na(country))
 
+wh_wk_country_prop_hist <- 
+ggplot(wh_wiki_table_location_prop,
+       aes(prop_sites_with_pages)) +
+  geom_histogram() +
+  theme_nogrid(10)
+
+wh_wk_country_all_counts <- 
+wh_wiki_table_location %>% 
+  count(country) %>% 
+  filter(!is.na(country)) %>% 
+  left_join(wh_wiki_table_location_prop)
+
+wh_wk_country_prop_scatter <- 
+ggplot(wh_wk_country_all_counts,
+       aes(prop_sites_with_pages, n)) +
+  geom_point() +
+  coord_fixed(0.02) +
+  theme_nogrid(6)
+
+wh_wk_country_prop_scatter_marginal <- 
+ggExtra::ggMarginal(wh_wk_country_prop_scatter,
+                    type = "histogram")
+
+sf_map_data_prop <- 
+world %>% 
+  filter(name != "Antartica") %>% 
+  left_join(wh_wiki_table_location_prop,
+            by = c( 'name' = 'country')) %>% 
+  select(name, prop_sites_with_pages, geometry)
+
+wh_wk_country_prop_map <- 
+ggplot(data = sf_map_data_prop) +
+    geom_sf(aes(fill = prop_sites_with_pages)) +
+    scale_fill_viridis_c(na.value="grey90") +
+  coord_sf() +
+  theme_minimal()
+
+wh_wk_country_prop_map +
+  annotation_custom((wh_wk_country_prop_scatter_marginal), 
+                    xmin = -190, 
+                    xmax = -90, 
+                    ymin= 10, 
+                    ymax=-70) 
 ```

### 2019-02-26 code/paper.Rmd
maps

@@
 # all WH sites with WP pages (n = 584)
-page_data_for_all_pages <- readRDS("data/page_data_for_all_pages.rds")
+page_data_for_all_pages <- 
+  readRDS(here::here("data", 
+                     "page_data_for_all_pages.rds"))
 
 # all WH sites, with and without WP pages (n = 846)
-wh_wiki_table <- read_csv('data/wh_wiki_table.csv')
+wh_wiki_table <- 
+  read_csv(here::here("data", 
+                      "wh_wiki_table.csv"))
+
+# all WH sites according to UNESCO
+# from https://whc.unesco.org/en/syndication
+wh_unesco <- readxl::read_excel(here::here("data",
+                                           "whc-sites-2018.xls")) %>% 
+  filter(category %in% c("Cultural", "Mixed"))
+
+library("rnaturalearth")
+library("rnaturalearthdata")
+world <- ne_countries(scale = "medium", returnclass = "sf")
+
+# functions used more than once:
+
+estimate_mode <- function(x) {
+  d <- density(x)
+  d$x[which.max(d$y)]
+}
+
+theme_nogrid <- function (base_size = 12, base_family = "") {
+  theme_bw(base_size = base_size, 
+           base_family = base_family) %+replace% 
+    theme(panel.grid = element_blank() )   
+}
+```
+
+## Representation by country
+
+Where are the WH sites, before looking into WP
+
+```{r}
+
+wh_unesco_countries <- 
+wh_unesco %>% 
+  separate_rows(states_name_en, convert = TRUE, sep = ",") %>% 
+  mutate(country = case_when(
+    states_name_en == "Bolivia (Plurinational State of)"  ~ "Bolivia",
+    states_name_en == "Cabo Verde"  ~ "Republic of Cabo Verde",
+    states_name_en == "Czechia"  ~ "Czech Republic",
+    states_name_en == "Democratic People's Republic of Korea"  ~ "Republic of Korea",
+    states_name_en == "Gambia (the)"  ~ "The Gambia",
+    states_name_en == "Holy See"  ~ "Vatican",
+    states_name_en == "Iran (Islamic Republic of)"  ~ "Iran",
+    states_name_en == "Lao People's Democratic Republic"  ~ "Lao PDR",
+    states_name_en == "Micronesia (Federated States of)"  ~ "Federated States of Micronesia",
+    states_name_en == "Syrian Arab Republic"  ~ "Syria",
+    states_name_en == "the former Yugoslav Republic of Macedonia"  ~ "Macedonia",
+    states_name_en == "United Kingdom of Great Britain and Northern Ireland"  ~ "United Kingdom",
+    states_name_en == "United Republic of Tanzania"  ~ "Tanzania",
+    states_name_en == "United States of America"  ~ "United States",
+    states_name_en == "Venezuela (Bolivarian Republic of)"  ~ "Venezuela",
+    states_name_en == "United States of America"  ~ "United States",
+    states_name_en == "Viet Nam"  ~ "Vietnam",
+    states_name_en == "Republic of Moldova"  ~ "Moldova",
+    TRUE ~ as.character(states_name_en)
+  ))
+
+wh_unesco_countries_count <-  
+  wh_unesco_countries %>% 
+  count(country)
+
+median_number_unesco_sites_per_country <- 
+  median(wh_unesco_countries_count$n)
+
+mode_number_unesco_sites_per_country <- 
+  round(estimate_mode(wh_unesco_countries_count$n), 1)
+
+wh_unesco_country_counts_hist <- 
+ggplot(wh_unesco_countries_count,
+       aes(n)) +
+  geom_histogram() +
+  annotate("text", x = 30, y = 30, 
+           label = str_glue('Median = {median_number_unesco_sites_per_country} WH sites/country\nMode = {mode_number_unesco_sites_per_country} WH sites/country'),
+           size = 3) +
+  theme_nogrid(12)
+
+sf_map_data_unesco <- 
+world %>% 
+  left_join(wh_unesco_countries_count,
+            by = c( 'name_long' = 'country')) %>% 
+  select(name, n, geometry) %>% 
+  mutate(n = ifelse(is.na(n), 0, n)) %>% 
+  filter(name != "Antartica")
+
+wh_country_unesco_count_map <- 
+ggplot(data = sf_map_data_unesco) +
+    geom_sf(aes(fill = n), lwd = 0) +
+    scale_fill_viridis_c(na.value="grey90") +
+  coord_sf() +
+  coord_sf(ylim = c(-50, 90), datum = NA) +
+  theme_minimal()
+
+wh_country_unesco_count_map +
+  annotation_custom(ggplotGrob(wh_unesco_country_counts_hist), 
+                    xmin = -190, 
+                    xmax = -90, 
+                    ymin= 10, 
+                    ymax=-70)
 
@@
 ```{r}
-library("rnaturalearth")
-library("rnaturalearthdata")
-world <- ne_countries(scale = "medium", returnclass = "sf")
-
   # get country of site from location text
@@
 world %>% 
-  filter(name != "Antartica") %>% 
   left_join(wh_wk_country_counts,
             by = c( 'name' = 'country')) %>% 
-  select(name, n, geometry)
+  select(name, n, geometry) %>% 
+  mutate(n = ifelse(is.na(n), 0, n)) %>% 
+  filter(name != "Antartica")
 
@@
 ggplot(data = sf_map_data) +
-    geom_sf(aes(fill = n)) +
+    geom_sf(aes(fill = n), lwd = 0) +
     scale_fill_viridis_c(na.value="grey90") +
   coord_sf() +
+  coord_sf(ylim = c(-50, 90), datum = NA) +
   theme_minimal()
-```
 
-Combine map and histogram
-
-```{r}
 wh_wk_country_count_map +
@@
        aes(prop_sites_with_pages, n)) +
-  geom_point() +
+  geom_point(alpha = 0.5) +
   coord_fixed(0.02) +
@@
             by = c( 'name' = 'country')) %>% 
-  select(name, prop_sites_with_pages, geometry)
+  select(name, 
+         prop_sites_with_pages, 
+         geometry)  %>% 
+  mutate(prop_sites_with_pages = ifelse(is.na(prop_sites_with_pages), 0, prop_sites_with_pages))
 
@@
 ggplot(data = sf_map_data_prop) +
-    geom_sf(aes(fill = prop_sites_with_pages)) +
+    geom_sf(aes(fill = prop_sites_with_pages), lwd = 0) +
     scale_fill_viridis_c(na.value="grey90") +
   coord_sf() +
+  coord_sf(ylim = c(-50, 90), datum = NA) +
   theme_minimal()
@@
 ```
+
+## Basic qualities of the WP articles about WH sites
+
+Length: correlate with ??
+number of links out/word
+number of references/word: scholarly or not
+
+## Basic qualitites of attention paid to articles
+
+number of links in
+page_views_last_n_days_total
+
+## Basic qualities of the editing process
+
+number of edits, total, prop/words
+size of edits
+divesity of editors
+
+## Locality
+
+IP addresses
+
+## Networks
+
+editors
+
+## Controversies
+
+time between edits
+edit reverts
+talk page: length and sentiment
+
+## Technicity
+
+bots
 

### 2019-02-26 code/paper.Rmd
graphs

@@
 
+```{r}
+# load the random pages
+ten_k_random_wp_pages <- readRDS(here::here("data", "random_page_data_tbl.rds"))
+
+ten_k_random_wp_pages_basic_qualities <- 
+ten_k_random_wp_pages %>% 
+  select(page_wordcount,
+         page_wikilinks_out, 
+         page_cited_items_on) %>% 
+  mutate(rnd_page_wikilinks_out_per_1k_words = page_wikilinks_out / page_wordcount * 1000,
+         rnd_page_cited_items_on_per_1k_words = page_cited_items_on / page_wordcount * 1000,
+         rnd_page_wordcount = page_wordcount) %>% 
+  select(-page_wikilinks_out,
+         -page_cited_items_on,
+         -page_wordcount)
+
+ten_k_random_wp_pages_basic_qualities_long <- 
+  ten_k_random_wp_pages_basic_qualities %>% 
+  gather(variable, value) 
+```
+
 Length: correlate with ??
@@
 number of references/word: scholarly or not
+
+```{r}
+page_data_for_all_pages_basic_qualities <- 
+page_data_for_all_pages %>% 
+  select(page_wordcount,
+         page_wikilinks_out, 
+         page_cited_items_on) %>% 
+  mutate(page_wikilinks_out_per_1k_words = page_wikilinks_out / page_wordcount * 1000,
+         page_cited_items_on_per_1k_words = page_cited_items_on / page_wordcount * 1000) %>% 
+  select(-page_wikilinks_out,
+         -page_cited_items_on)
+
+page_data_for_all_pages_basic_qualities_long <- 
+page_data_for_all_pages_basic_qualities %>% 
+  gather(variable, value) %>% 
+  bind_rows(ten_k_random_wp_pages_basic_qualities_long) %>% 
+  mutate(source = ifelse(str_detect(variable, "rnd" ), "10k Random pages", "World Heritage pages")) %>% 
+  mutate(variable = str_remove(variable, "rnd_"))
+
+# density plots
+  ggplot(page_data_for_all_pages_basic_qualities_long,
+         aes(value)) +
+  geom_density(aes(fill = source),
+               alpha = 0.3) +
+  scale_x_log10() +
+  scale_fill_viridis_d() +
+  facet_wrap( ~ variable, 
+              scales = "free") +
+  theme_minimal()
+```
+
+```{r}
+# scatterplots
+  ggplot() +
+      geom_point(data = ten_k_random_wp_pages_basic_qualities,
+             aes(rnd_page_wikilinks_out_per_1k_words,
+                 rnd_page_cited_items_on_per_1k_words,
+                 size = rnd_page_wordcount),
+             colour = "grey80",
+             alpha = 0.4) +
+  geom_point(data = page_data_for_all_pages_basic_qualities,
+             aes(page_wikilinks_out_per_1k_words,
+                 page_cited_items_on_per_1k_words,
+                 size = page_wordcount),
+             colour = "red",
+             alpha = 0.8) +
+  scale_x_log10() +
+  scale_y_log10() +
+  scale_fill_viridis_d() +
+  coord_fixed() +
+  theme_minimal()
+
+```
 
@@
 page_views_last_n_days_total
+
+```{r}
+ten_k_random_wp_pages_attent <- 
+ten_k_random_wp_pages %>% 
+  select(page_wikilinks_in, 
+         page_views_last_n_days_total)
+
+page_data_for_all_pages_attent <- 
+page_data_for_all_pages %>% 
+  select(page_wikilinks_in, 
+         page_views_last_n_days_total)
+
+page_data_for_all_pages %>% 
+  select( Site,
+         page_wikilinks_in, 
+         page_views_last_n_days_total)  %>% 
+  ggplot(aes(page_wikilinks_in,
+             page_views_last_n_days_total,
+             label = Site)) +
+  geom_point(alpha = 0.4) +
+    geom_text_repel(
+    data          = page_data_for_all_pages %>%  
+                           filter(page_views_last_n_days_total > 190000),
+    segment.size  = 0.2,
+    segment.color = "grey50",
+    direction     = "both"
+  ) +
+  scale_y_log10(expand = c(1, 0.05)) +
+  scale_x_log10(limits = c(1, 10000)) +
+  coord_fixed(0.5) +
+  theme_minimal()
+
+page_data_for_all_pages_attent_long <- 
+page_data_for_all_pages_attent %>% 
+  gather(variable, value) %>% 
+  bind_rows(ten_k_random_wp_pages_attent %>% 
+              gather(variable, value) %>% 
+              mutate(variable =  str_glue('rnd_{variable}'))) %>% 
+  mutate(source = ifelse(str_detect(variable, "rnd" ), "10k Random pages", 
+                         "World Heritage pages")) %>% 
+  mutate(variable = str_remove(variable, "rnd_"))
+
+# density plots
+  ggplot(page_data_for_all_pages_attent_long,
+         aes(value)) +
+  geom_density(aes(fill = source),
+               alpha = 0.3) +
+  scale_x_log10() +
+  scale_fill_viridis_d() +
+  facet_wrap( ~ variable, 
+              scales = "free") +
+  theme_minimal()
+```
 

### 2019-02-28 code/000-scrape-wikipedia.R
get 10k edits and 10k links in

@@ -295,7 +295,7 @@ get_data_about_page <- function(the_page) {
     html_attr('href') %>% 
     str_remove("/wiki/") %>% 
     str_glue("https://en.wikipedia.org/w/index.php?title=",.,
-             "&limit=1000") %>% 
+             "&limit=10000") %>% 
     read_html() %>% 
     html_nodes("#mw-whatlinkshere-list li > a") %>% 
     html_attr('href') %>% 
@@ -315,7 +315,7 @@ get_data_about_page <- function(the_page) {
     html_attr('href') %>% 
     str_glue("https://en.wikipedia.org",.) %>% 
     str_replace("&action=history", 
-                "&offset=&limit=2000&action=history")
+                "&offset=&limit=10000&action=history")
 
   
   rh_date = revision_history_page %>% 
@@ -500,6 +500,9 @@ return(region_tbl_coords_links_info_flat)
 get_various_page_data_for_all_pages_safe <- 
   safely(get_various_page_data_for_all_pages, 
          otherwise = "some_problem")
+
+
+wh_wiki_table <- readr::read_csv("data/wh_wiki_table.csv")
 
 # this takes several hours
 page_data_for_all_pages <- 

### 2019-03-01 code/paper.Rmd
exploring edit data

@@
 library(tidyverse)
+
+# load the random pages
+ten_k_random_wp_pages <- readRDS(here::here("data", "random_page_data_tbl.rds"))
 
@@
 ```{r}
-# load the random pages
-ten_k_random_wp_pages <- readRDS(here::here("data", "random_page_data_tbl.rds"))
-
 ten_k_random_wp_pages_basic_qualities <- 
@@
 
+```{r}
+revision_history_page_details <- 
+  tibble(revision_history_page_details = map(page_data_for_all_pages$page_info_t, 
+      ~.x$revision_history_page_details)) %>% 
+  mutate(Site =         page_data_for_all_pages$Site,
+         Country =      page_data_for_all_pages$country,
+         rh_n_editors = map_int(revision_history_page_details, ~n_distinct(.x$rh_user)),
+         rh_n_edits =   map_int(revision_history_page_details, ~nrow(.x)),
+         rh_user_simpson_idx = page_data_for_all_pages$rh_user_simpson_idx,
+         rh_user_bot_prop = page_data_for_all_pages$rh_user_bot_prop,
+         rh_revert_prop = page_data_for_all_pages$rh_revert_prop)
+
+# load the random pages revision histories
+ten_k_random_wp_pages_lst <- readRDS(here::here("data", "random_page_data_lst.rds"))
+
+ggplot(revision_history_page_details,
+       aes(rh_n_edits)) +
+  geom_histogram()
+
+```
+
 ## Locality
@@
 IP addresses
+
+```{r}
+
+get_ip_addresses <- function(x){
+  re <- regexpr(
+  "(?(?=.*?(\\d+\\.\\d+\\.\\d+\\.\\d+).*?)(\\1|))", 
+  x, perl = TRUE)
+regmatches(x, re)
+}
+
+# get locations from IP addresses
+library(rgeolocate)
+ip_db <- system.file("extdata","GeoLite2-Country.mmdb", package = "rgeolocate")
+
+revision_history_page_details_ip_addresses <- 
+revision_history_page_details %>% 
+  mutate(edits_from_ip_addresses = map(revision_history_page_details,
+                          ~.x %>% 
+                            filter(get_ip_addresses(rh_user) != "") %>% 
+                            mutate(ip_location = map(rh_user, 
+                                                     ~maxmind(.x, ip_db)))  %>% 
+                            unnest(ip_location)))
+
+# analyse the countries of IP address vs country of WH site
+revision_history_page_details_ip_addresses_df <- 
+revision_history_page_details_ip_addresses %>% 
+  unnest(edits_from_ip_addresses)
+
+revision_history_page_details_ip_addresses_countries <- 
+revision_history_page_details_ip_addresses_df %>% 
+  select(Site, Country, country_name, rh_n_edits ) %>% 
+  filter_all(all_vars(!is.na(.))) %>% 
+  group_by(Site, Country, rh_n_edits) %>% 
+  count(country_name) %>% 
+  mutate(prop_anon_of_all_edits = n / rh_n_edits) %>% 
+  mutate(internal_edits = ifelse(Country ==  country_name, 
+                                 TRUE, FALSE),
+         n_anon_edits_total = n) %>% 
+  left_join(revision_history_page_details_ip_addresses_df) %>% 
+  distinct(Site,  
+           Country, 
+           prop_anon_of_all_edits, 
+           internal_edits,
+           .keep_all = TRUE) %>% 
+  group_by(Site,  Country) %>% 
+  summarise(sum_prop_internal = sum(n_anon_edits_total[internal_edits]) / sum(n_anon_edits_total),
+            sum_prop_external = 1 - sum_prop_internal,
+            rh_n_edits = unique(rh_n_edits),
+            rh_n_edits_anon = sum(n_anon_edits_total),
+            prop_anon_of_all_edits = sum(n) / rh_n_edits)
+```
+
+```{r}
+# Histogram of proportion of anonymous edits 
+# TODO and random sites
+ggplot(revision_history_page_details_ip_addresses_countries,
+       aes(prop_anon_of_all_edits)) +
+  geom_histogram() +
+  theme_minimal()
+```
+
+```{r}
+# Histogram of proportion of all anonymous edits that come from same country as WH site
+ggplot(revision_history_page_details_ip_addresses_countries,
+       aes(sum_prop_internal)) +
+  geom_histogram() +
+  theme_minimal() 
+```
+
+```{r}
+ggplot(revision_history_page_details_ip_addresses_countries,
+       aes(sum_prop_internal,
+           prop_anon_of_all_edits)) +
+  geom_point() +
+  theme_minimal() +
+  coord_equal()
+
+```
+
+ggplot(revision_history_page_details_ip_addresses_countries, 
+       aes(sum_prop_internal, 
+           prop_anon_of_all_edits)) +
+  geom_point() +
+  scale_x_log10() +
+  scale_y_log10() +
+  theme_minimal()
+
+```
 

### 2019-03-11 code/000-scrape-wikipedia.R
load rnd pages earlier

@@ -512,6 +512,8 @@ page_data_for_all_pages <-
 page_data_for_all_pages$result %>% 
   select_if(is.numeric)
 
+page_data_for_all_pages_result <- page_data_for_all_pages$result 
+
 # save it
 saveRDS(page_data_for_all_pages$result, 
         'data/page_data_for_all_pages.rds')

### 2019-03-11 code/000-scrape-wikipedia-random-pages.R
stash

@@ -6,7 +6,7 @@ library(vegan)
 rando <- "https://en.wikipedia.org/wiki/Special:Random"
 
 # gets data about n WP pages
-n <- 10000
+n <- 100000
 random_page_data <- rerun(n, get_data_about_page_safe(rando) )
 
 # drops the pages that returned an error

### 2019-03-11 code/000-scrape-wikipedia.R

@@ -512,8 +512,10 @@ page_data_for_all_pages <-
 page_data_for_all_pages$result %>% 
   select_if(is.numeric)
 
+page_data_for_all_pages_result <- page_data_for_all_pages$result
+
 # save it
-saveRDS(page_data_for_all_pages$result, 
+saveRDS(page_data_for_all_pages_result, 
         'data/page_data_for_all_pages.rds')
 
 

### 2019-03-16 code/paper.Rmd
circle chord plot

@@
 ten_k_random_wp_pages <- readRDS(here::here("data", "random_page_data_tbl.rds"))
+
+# load the random pages revision histories
+ten_k_random_wp_pages_lst <- readRDS(here::here("data", "random_page_data_lst.rds"))
 
@@
 
-# load the random pages revision histories
-ten_k_random_wp_pages_lst <- readRDS(here::here("data", "random_page_data_lst.rds"))
-
 ggplot(revision_history_page_details,
@@
 
-ggplot(revision_history_page_details_ip_addresses_countries, 
-       aes(sum_prop_internal, 
-           prop_anon_of_all_edits)) +
-  geom_point() +
-  scale_x_log10() +
-  scale_y_log10() +
-  theme_minimal()
+```{r}
+adjacency_list_3_cols <- 
+revision_history_page_details_ip_addresses_df %>% 
+  filter(!is.na(Country),
+         !is.na(country_name)) %>% 
+  group_by(Country, country_name) %>% 
+  count() %>% 
+  rename(to = Country,
+         from = country_name,
+         value = n) %>% 
+  ungroup() %>% 
+  mutate(from = ifelse(from == "Hashemite Kingdom of Jordan", "Jordan", from)) %>% 
+  select(from, to , value) %>% 
+  filter(value > 100) %>% 
+  left_join( revision_history_page_details_ip_addresses_df %>% 
+               select(country_name, continent_name) %>% 
+               distinct(),
+             by = c('from' = 'country_name')) %>% 
+  arrange(continent_name,  from, to)
+
+adjacency_list <- 
+adjacency_list_3_cols%>% 
+  select(-continent_name)
+
+get_countries_in_continent <- function(x) {
+
+  xx <- 
+  revision_history_page_details_ip_addresses_df %>% 
+    select(country_name, continent_name) %>% 
+    filter(continent_name == x) %>% 
+    pull(country_name) %>% 
+    unique()
+
+  xx[
+ unique( c(adjacency_list$from,
+           adjacency_list$to))
+ ]
+}
+
+africa   <- get_countries_in_continent("Africa")        
+asia    <- get_countries_in_continent("Asia")       
+europe  <-get_countries_in_continent("Europe")  
+north_america  <- get_countries_in_continent("North America")         
+oceania <-  get_countries_in_continent("Oceania") 
+south_america  <-  get_countries_in_continent("South America")
+
+library(circlize)
+circos.clear()
+chordDiagram(adjacency_list, 
+             directional = 1,
+             direction.type = c("diffHeight", "arrows"),
+             link.arr.type = "big.arrow", 
+             diffHeight = -uh(2, "mm"),
+             annotationTrack = "grid", 
+             preAllocateTracks = list(track.height = max(0.4)))
+
+# we go back to the first track and customize sector labels
+circos.track(track.index = 1, panel.fun = function(x, y) {
+    circos.text(CELL_META$xcenter, CELL_META$ylim[1], CELL_META$sector.index, 
+        facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
+}, bg.border = NA) # here set bg.border to NA is important
+
+highlight.sector(africa, track.index = 1, col = "#00FF0040", 
+    text = "Africa", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(asia, track.index = 1, col = "#0000FF40", 
+    text = "Asia", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(europe, track.index = 1, col = "blue", 
+    text = "Europe", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(north_america, track.index = 1, col = "orange", 
+    text = "North America", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(oceania, track.index = 1, col = "purple", 
+    text = "Oceania", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(south_america, track.index = 1, col = "brown", 
+    text = "South America", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+#-- 
+circos.track(track.index = 2, panel.fun = function(x, y) {
+    sector.index = get.cell.meta.data("sector.index")
+    xlim = get.cell.meta.data("xlim")
+    ylim = get.cell.meta.data("ylim")
+    circos.text(mean(xlim), mean(ylim), sector.index, cex = 0.6, niceFacing = TRUE)
+}, bg.border = NA)
+
+#--
+circos.clear()
+circos.par(gap.after = rep(c(rep(1, 4), 8), 3))
+
+chordDiagram(adjacency_list, annotationTrack = c("grid", "axis"),
+    preAllocateTracks = list(
+        track.height = uh(4, "mm"),
+        track.margin = c(uh(4, "mm"), 0)
+))
+
+circos.track(track.index = 2, panel.fun = function(x, y) {
+    sector.index = get.cell.meta.data("sector.index")
+    xlim = get.cell.meta.data("xlim")
+    ylim = get.cell.meta.data("ylim")
+    circos.text(mean(xlim), mean(ylim), sector.index, cex = 0.6, niceFacing = TRUE)
+}, bg.border = NA)
+
+highlight.sector(africa, track.index = 1, col = "red", 
+    text = "Africa", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(asia, track.index = 1, col = "green", 
+    text = "Asia", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(europe, track.index = 1, col = "blue", 
+    text = "Europe", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(north_america, track.index = 1, col = "orange", 
+    text = "North America", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(oceania, track.index = 1, col = "purple", 
+    text = "Oceania", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(south_america, track.index = 1, col = "brown", 
+    text = "South America", cex = 0.8, text.col = "white", niceFacing = TRUE)
 

### 2019-03-16 code/000-scrape-wikipedia-random-pages.R

@@ -6,7 +6,7 @@ library(vegan)
 rando <- "https://en.wikipedia.org/wiki/Special:Random"
 
 # gets data about n WP pages
-n <- 100000
+n <- 10000
 random_page_data <- rerun(n, get_data_about_page_safe(rando) )
 
 # drops the pages that returned an error
@@ -33,3 +33,8 @@ random_page_data_tbl %>%
   geom_histogram() +
   facet_wrap( ~ variable, scales = "free")
 
+
+
+saveRDS(random_page_data_tbl, "data/random_page_data_tbl.rds")
+
+saveRDS(random_page_data_lst, "data/random_page_data_lst.rds")

### 2019-03-16 code/000-scrape-wikipedia.R

@@ -502,7 +502,7 @@ get_various_page_data_for_all_pages_safe <-
          otherwise = "some_problem")
 
 
-wh_wiki_table <- readr::read_csv("data/wh_wiki_table.csv")
+wh_wiki_table <- readr::read_csv("../data/wh_wiki_table.csv")
 
 # this takes several hours
 page_data_for_all_pages <- 
@@ -516,7 +516,7 @@ page_data_for_all_pages_result <- page_data_for_all_pages$result
 
 # save it
 saveRDS(page_data_for_all_pages_result, 
-        'data/page_data_for_all_pages.rds')
+        '../data/page_data_for_all_pages.rds')
 
 
 

### 2019-03-29 code/paper.Rmd
exploring edit controversy in random pages

--- 2019-03-01 code/paper.Rmd
@@
 
+ip_regex <- "(?(?=.*?(\\d+\\.\\d+\\.\\d+\\.\\d+).*?)(\\1|))"
+
 get_ip_addresses <- function(x){
   re <- regexpr(
-  "(?(?=.*?(\\d+\\.\\d+\\.\\d+\\.\\d+).*?)(\\1|))", 
+  ip_regex, 
   x, perl = TRUE)
@@
 
+```
+
+Do WH sites have more geographically diverse contributions?
+
+Get locations for random pages.
+
+How many IP edits on each page?
+
+```{r}
+randoms_revision_history_page_details <- 
+  map_df(ten_k_random_wp_pages_lst, 
+         ~.x$revision_history_page_details, 
+         .id = "page")
+
+randoms_revision_history_page_details_ip <- 
+randoms_revision_history_page_details %>% 
+    mutate(is_ip_address = ifelse(get_ip_addresses(rh_user) != "", TRUE, FALSE),
+         page = as.numeric(page))
+
+randoms_revision_history_page_details_ip_prop <- 
+  randoms_revision_history_page_details_ip %>% 
+  group_by(page) %>% 
+  summarise(prop_ip_addresses = sum(is_ip_address) / n() )
+
+ggplot(randoms_revision_history_page_details_ip_prop,
+       aes(prop_ip_addresses)) +
+  geom_histogram() +
+  theme_minimal()
+```
+
+Overall location of IP edits for all random pages
+
+```{r}
+randoms_revision_history_page_details_ip_location <- 
+randoms_revision_history_page_details_ip %>% 
+  filter(is_ip_address) %>% 
+  mutate(ip_location = map(rh_user, ~maxmind(.x, ip_db)))  %>% 
+  unnest(ip_location)
+
+randoms_revision_history_page_details_ip_location_tally <- 
+randoms_revision_history_page_details_ip_location %>% 
+  filter(!is.na(country_name)) %>% 
+  mutate(country_name = fct_rev(fct_infreq(country_name))) %>% 
+  group_by(country_name) %>% 
+  tally(sort = TRUE) %>% 
+  filter(n > 100)
+
+ggplot(randoms_revision_history_page_details_ip_location_tally,
+       aes(country_name, n)) +
+  geom_col() +
+  coord_flip()   +
+  theme_minimal() +
+  scale_y_continuous(labels = scales::comma)
+```
+
+What's the geographic diversity of edits per random page?
+
+```{r}
+randoms_revision_history_page_details_ip_location_props_per_page <- 
+randoms_revision_history_page_details_ip_location %>% 
+  filter(!is.na(country_name)) %>% 
+  mutate(country_name = fct_rev(fct_infreq(country_name))) %>% 
+  group_by(page, country_name) %>% 
+  tally() %>% 
+  mutate(prop = n / sum(n)) 
+  filter(country_name %in% randoms_revision_history_page_details_ip_location_tally$country_name)
+
+ggplot(randoms_revision_history_page_details_ip_location_props_per_page,
+       aes(country_name, 
+           prop)) +
+  geom_boxplot() +
+  coord_flip()
+
+randoms_revision_history_page_details_ip_location_props_per_page_div <- 
+  randoms_revision_history_page_details_ip_location_props_per_page %>% 
+  group_by(page) %>% 
+  summarise(shannon = vegan::diversity(n))
+
+ggplot(randoms_revision_history_page_details_ip_location_props_per_page_div,
+       aes( shannon)) +
+  geom_histogram() 
+```
+
+```{r}
+
+revision_history_page_details_ip_addresses <- 
+randoms_revision_history_page_details %>% 
+  mutate()
+  mutate(edits_from_ip_addresses = map(revision_history_page_details,
+                          ~.x %>% 
+                            filter(get_ip_addresses(rh_user) != "") %>% 
+                            mutate(ip_location = map(rh_user, 
+                                                     ~maxmind(.x, ip_db)))  %>% 
+                            unnest(ip_location)))
+
+```
+
+```{r}
+# analyse the countries of IP address vs country of WH site
 revision_history_page_details_ip_addresses <- 
@@
 
-# analyse the countries of IP address vs country of WH site
 revision_history_page_details_ip_addresses_df <- 
@@
 
-```
-
 ggplot(revision_history_page_details_ip_addresses_countries, 
@@
 
+Look at distributions of variables, then say 2sd is extreme, and match those to the WH pages to find out what they are
+
+What's the typical distribution of talk page length?
+
+```{r}
+ten_k_random_wp_pages %>% 
+  mutate(tp_divided_by_page_word_count = talk_page_wordcount / page_wordcount) %>% 
+  ggplot(aes(talk_page_wordcount)) +
+  geom_histogram() +
+  scale_x_log10(labels = scales::comma_format(accuracy = 0.01))
+```
+
+Can we detect -ve sentiment on the talk pages? Perhaps as distributions, over every 100 words per page
+
+```{r}
+library(tidytext)
+
+```
+
+What's the typical distribution of the proportion of edits that are reverts?
+
+```{r}
+ggplot(ten_k_random_wp_pages,
+       aes(rh_revert_prop)) +
+  geom_histogram() +
+  scale_x_log10()
+
+```
+
+What are the keywords for controversy in edit messages? And how common are these warrning messages?
+
+```{r}
+randoms_revision_history_page_details_ip_warring_words <- 
+randoms_revision_history_page_details_ip %>% 
+  mutate(warring_words = (str_detect(rh_comment, 'undid|vandalism|why|inaccurate|wrong|warning|blocked|warring|disputed|neutral|unacceptable' )))
+
+# distribution of edits with warring words
+randoms_revision_history_page_details_ip_warring_words_prop <- 
+randoms_revision_history_page_details_ip_warring_words %>% 
+  group_by(page) %>% 
+  summarise(prop_warring_edits = sum(warring_words) / n())
+
+ggplot(randoms_revision_history_page_details_ip_warring_words_prop,
+         aes(prop_warring_edits)) +
+  geom_histogram() +
+  scale_x_log10()
+```
+
+Is there are correlation between the proportion of warring words and talk page length?
+
+```{r}
+# some interesting groupings
+randoms_revision_history_page_details_ip_warring_words_prop %>% 
+  left_join(ten_k_random_wp_pages %>% 
+  mutate(page = 1:nrow(.))) %>% 
+  filter(prop_warring_edits > 0) %>% 
+  ggplot(aes(prop_warring_edits, 
+             talk_page_wordcount ,
+             size = page_wordcount)) +
+  geom_point(alpha = 0.2)
+```
+
+Is there are correlation between the proportion of warring words and revert frequency?
+
+```{r}
+randoms_revision_history_page_details_ip_warring_words_prop_revert_prop <- 
+randoms_revision_history_page_details_ip_warring_words_prop %>% 
+  left_join(ten_k_random_wp_pages %>% 
+  mutate(page = 1:nrow(.))) %>% 
+  filter(prop_warring_edits != 0,
+         rh_revert_prop != 0)
+
+lm(rh_revert_prop ~ prop_warring_edits, 
+   data = randoms_revision_history_page_details_ip_warring_words_prop_revert_prop) %>% summary
+
+ggplot(randoms_revision_history_page_details_ip_warring_words_prop_revert_prop,
+         aes(prop_warring_edits, 
+             rh_revert_prop)) +
+  geom_point()
+```
+
+can we identify a cluster of controversial pages? Not really
+
+```{r}
+
+randoms_revision_history_page_details_ip_warring_words_prop_clus <- 
+randoms_revision_history_page_details_ip_warring_words_prop %>% 
+  left_join(ten_k_random_wp_pages %>% 
+  mutate(page = 1:nrow(.))) %>% 
+  select(rh_revert_prop, 
+         prop_warring_edits,
+         rh_diff_size_cv) %>%
+   filter_all(all_vars(!is.na(.))) %>% 
+  princomp(., scale = TRUE)
+
+```
+
 time between edits
-edit reverts
-talk page: length and sentiment
+
+```{r}
+library(lubridate)
+randoms_revision_history_page_details_ip_time_diffs <- 
+randoms_revision_history_page_details_ip %>% 
+  group_nest(page) %>% 
+  mutate(time_diff = map(data, ~lag(.x$rh_date) - .x$rh_date)) %>% 
+  unnest(time_diff) %>% 
+  mutate(time_diff_days = as.numeric(time_diff / 60 / 60 / 24)) %>% 
+  mutate(time_diff_hours = as.numeric(time_diff / 60 / 60 )) %>% 
+  mutate(less_than_one_month = ifelse(time_diff_hours < 744, TRUE, FALSE)) %>% 
+  mutate(less_than_one_week = ifelse(time_diff_hours < 168, TRUE, FALSE)) %>% 
+  bind_cols(randoms_revision_history_page_details_ip)
+
+rle_tbl <- 
+tibble(lths = rle(randoms_revision_history_page_details_ip_time_diffs$rh_user)$lengths,
+vals = rle(randoms_revision_history_page_details_ip_time_diffs$rh_user)$values)
+
+rle_tbl2 <- tibble(
+  rh_user = rep(rle_tbl$vals, rle_tbl$lths),
+  lths2 = rep(rle_tbl$lths, rle_tbl$lths)
+)
+
+randoms_revision_history_page_details_ip_time_diffs %>% 
+  filter(!is.na(time_diff_hours)) %>% 
+  mutate(quick_three_edits = time_diff_hours + lag(time_diff_hours) + lag(time_diff_hours, 2) + lag(time_diff_hours, 3)) %>% View
+
+randoms_revision_history_page_details_ip_time_diffs_quick <- 
+randoms_revision_history_page_details_ip_time_diffs %>% 
+ nest(-page) %>%  
+ mutate(edits_3 = map(data, ~.x %>% 
+                              filter(less_than_one_week) %>% 
+                              filter(n() > 4 ))) %>% 
+  unnest(edits_3)
+
+randoms_revision_history_page_details_ip_time_diffs %>% 
+  bind_cols(rle_tbl2) %>% 
+  filter(lths2 == 1) %>% 
+  filter(time_diff_hours < 24) %>% View
+
+ggplot(randoms_revision_history_page_details_ip_time_diffs,
+       aes(time_diff_days)) +
+  geom_histogram()
+
+```
 

### 2019-03-29 code/paper.Rmd
time series!

@@
 ```{r}
-
-revision_history_page_details_ip_addresses <- 
-randoms_revision_history_page_details %>% 
-  mutate()
-  mutate(edits_from_ip_addresses = map(revision_history_page_details,
-                          ~.x %>% 
-                            filter(get_ip_addresses(rh_user) != "") %>% 
-                            mutate(ip_location = map(rh_user, 
-                                                     ~maxmind(.x, ip_db)))  %>% 
-                            unnest(ip_location)))
-
-```
-
-```{r}
 # analyse the countries of IP address vs country of WH site
@@
 
+time series of edits: breakouts relating to events? monthly seems like a good level of aggregation. What can we do for spike detection?
+
+```{r}
+randoms_revision_history_page_details_ip_location %>% 
+  group_by(page) %>% 
+  mutate(the_d = floor_date(rh_date, "day")) %>% 
+    mutate(the_m = floor_date(rh_date, "month")) %>% 
+  group_by(page, the_m) %>% 
+  tally() %>% 
+  filter(n() > 130) %>%   # explore this value
+  ggplot() +
+  geom_line(aes(the_m,
+             n)) +
+  facet_wrap( ~ page, scales = "free")
+```
+
 ## Technicity

### 2019-03-30 code/paper.Rmd
anomaly analysis

@@
   tally() %>% 
-  mutate(prop = n / sum(n)) 
+  mutate(prop = n / sum(n)) %>% 
   filter(country_name %in% randoms_revision_history_page_details_ip_location_tally$country_name)
@@
 
-can we identify a cluster of controversial pages? Not really
-
-```{r}
-
-randoms_revision_history_page_details_ip_warring_words_prop_clus <- 
-randoms_revision_history_page_details_ip_warring_words_prop %>% 
-  left_join(ten_k_random_wp_pages %>% 
-  mutate(page = 1:nrow(.))) %>% 
-  select(rh_revert_prop, 
-         prop_warring_edits,
-         rh_diff_size_cv) %>%
-   filter_all(all_vars(!is.na(.))) %>% 
-  princomp(., scale = TRUE)
-
-```
-
 time between edits
@@
   filter(!is.na(time_diff_hours)) %>% 
-  mutate(quick_three_edits = time_diff_hours + lag(time_diff_hours) + lag(time_diff_hours, 2) + lag(time_diff_hours, 3)) %>% View
+  mutate(quick_three_edits = time_diff_hours + lag(time_diff_hours) + lag(time_diff_hours, 2) + lag(time_diff_hours, 3))
 
@@
   filter(lths2 == 1) %>% 
-  filter(time_diff_hours < 24) %>% View
+  filter(time_diff_hours < 24)
 
@@
   facet_wrap( ~ page, scales = "free")
+```
+
+Spike detection
+
+for randoms, what even is an anomaly?
+
+```{r}
+# devtools::install_github("hrbrmstr/AnomalyDetection")
+library(AnomalyDetection)
+randoms_revision_history_page_details_ip_location_monthly <- 
+randoms_revision_history_page_details_ip_location %>% 
+  group_by(page) %>% 
+  mutate(the_d = floor_date(rh_date, "day")) %>% 
+    mutate(the_m = floor_date(rh_date, "month")) %>% 
+  group_by(page, the_m) %>% 
+  tally() %>% 
+  filter(n() > 150) # explore this value
+
+randoms_revision_history_page_details_ip_location_monthly_anom <- 
+  randoms_revision_history_page_details_ip_location_monthly %>% 
+  ungroup %>% 
+  group_nest(page) %>% 
+  mutate(anomalies = map(data, ~ad_ts(.x, 
+                                      max_anoms = 0.2, 
+                                      alpha = 0.005,
+                                      threshold = "p95"))) %>% 
+  unnest(anomalies)
+
+ggplot() +
+  geom_line(
+    data=randoms_revision_history_page_details_ip_location_monthly %>% 
+      filter(page %in% randoms_revision_history_page_details_ip_location_monthly_anom$page), 
+    aes(the_m, n), 
+    size=0.125, color="lightslategray")  +
+  geom_point(
+    data=randoms_revision_history_page_details_ip_location_monthly_anom, 
+    aes(timestamp, anoms), 
+    color="#cb181d", alpha=1/3) +
+  scale_x_datetime(date_labels="%b\n%Y") +
+  facet_wrap( ~ page, scales = "free_y")
+
+```
+
+for WH sites
+
+```{r}
+revision_history_page_details_ip_addresses_df_monthly_edits <- 
+revision_history_page_details_ip_addresses_df  %>% 
+  mutate(the_d = floor_date(rh_date, "day")) %>% 
+    mutate(the_m = floor_date(rh_date, "month")) %>% 
+  group_by(Site, the_m) %>% 
+  tally() %>% 
+  filter(n() > 24) # explore this value
+
+# distribution of edits per month
+ggplot(revision_history_page_details_ip_addresses_df_monthly_edits,
+       aes(n)) +
+  geom_histogram() +
+  scale_x_log10()
+
+# subset so we get only sites with > 10 edits/month
+revision_history_page_details_ip_addresses_df_monthly_edits_10 <- 
+revision_history_page_details_ip_addresses_df_monthly_edits %>% 
+  filter(max(n) >= 10)
+
+```
+
+```{r}
+
+# detect anomalies
+revision_history_page_details_ip_addresses_df_monthly_edits_anoms <- 
+  revision_history_page_details_ip_addresses_df_monthly_edits_10 %>% 
+  ungroup %>% 
+  group_nest(Site) %>% 
+  mutate(anomalies = map(data, ~ad_ts(.x, 
+                                      max_anoms = 0.2, 
+                                      alpha = 0.005,
+                                      threshold = "p95"))) %>% 
+  unnest(anomalies) %>% 
+  group_by(Site) %>% 
+  filter(max(anoms) >= 50) # where the anomaly is 50 edits/month or more
+
+ggplot() +
+  geom_line(
+    data=revision_history_page_details_ip_addresses_df_monthly_edits_10 %>% 
+      filter(Site %in% revision_history_page_details_ip_addresses_df_monthly_edits_anoms$Site), 
+    aes(the_m, n), 
+    size=0.125, color="lightslategray")  +
+  geom_point(
+    data=revision_history_page_details_ip_addresses_df_monthly_edits_anoms, 
+    aes(timestamp, anoms), 
+    color="#cb181d", alpha=1/3) +
+  scale_x_datetime(date_labels="%b\n%Y") +
+  facet_wrap( ~ Site, scales = "free")
 ```

### 2019-03-30 code/paper.Rmd

@@
 
-ggplot(revision_history_page_details_ip_addresses_countries, 
-       aes(sum_prop_internal, 
-           prop_anon_of_all_edits)) +
-  geom_point() +
-  scale_x_log10() +
-  scale_y_log10() +
-  theme_minimal()
+```
+
+```{r}
+adjacency_list_3_cols <- 
+revision_history_page_details_ip_addresses_df %>% 
+  filter(!is.na(Country),
+         !is.na(country_name)) %>% 
+  group_by(Country, country_name) %>% 
+  count() %>% 
+  rename(to = Country,
+         from = country_name,
+         value = n) %>% 
+  ungroup() %>% 
+  mutate(from = ifelse(from == "Hashemite Kingdom of Jordan", "Jordan", from)) %>% 
+  select(from, to , value) %>% 
+  filter(value > 100) %>% 
+  left_join( revision_history_page_details_ip_addresses_df %>% 
+               select(country_name, continent_name) %>% 
+               distinct(),
+             by = c('from' = 'country_name')) %>% 
+  arrange(continent_name,  from, to)
+
+adjacency_list <- 
+adjacency_list_3_cols%>% 
+  select(-continent_name)
+
+get_countries_in_continent <- function(x) {
+
+  xx <- 
+  revision_history_page_details_ip_addresses_df %>% 
+    select(country_name, continent_name) %>% 
+    filter(continent_name == x) %>% 
+    pull(country_name) %>% 
+    unique()
+
+  xx[
+ unique( c(adjacency_list$from,
+           adjacency_list$to))
+ ]
+}
+
+africa   <- get_countries_in_continent("Africa")        
+asia    <- get_countries_in_continent("Asia")       
+europe  <-get_countries_in_continent("Europe")  
+north_america  <- get_countries_in_continent("North America")         
+oceania <-  get_countries_in_continent("Oceania") 
+south_america  <-  get_countries_in_continent("South America")
+
+library(circlize)
+circos.clear()
+chordDiagram(adjacency_list, 
+             directional = 1,
+             direction.type = c("diffHeight", "arrows"),
+             link.arr.type = "big.arrow", 
+             diffHeight = -uh(2, "mm"),
+             annotationTrack = "grid", 
+             preAllocateTracks = list(track.height = max(0.4)))
+
+# we go back to the first track and customize sector labels
+circos.track(track.index = 1, panel.fun = function(x, y) {
+    circos.text(CELL_META$xcenter, CELL_META$ylim[1], CELL_META$sector.index, 
+        facing = "clockwise", niceFacing = TRUE, adj = c(0, 0.5))
+}, bg.border = NA) # here set bg.border to NA is important
+
+highlight.sector(africa, track.index = 1, col = "#00FF0040", 
+    text = "Africa", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(asia, track.index = 1, col = "#0000FF40", 
+    text = "Asia", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(europe, track.index = 1, col = "blue", 
+    text = "Europe", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(north_america, track.index = 1, col = "orange", 
+    text = "North America", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(oceania, track.index = 1, col = "purple", 
+    text = "Oceania", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(south_america, track.index = 1, col = "brown", 
+    text = "South America", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+#-- 
+circos.track(track.index = 2, panel.fun = function(x, y) {
+    sector.index = get.cell.meta.data("sector.index")
+    xlim = get.cell.meta.data("xlim")
+    ylim = get.cell.meta.data("ylim")
+    circos.text(mean(xlim), mean(ylim), sector.index, cex = 0.6, niceFacing = TRUE)
+}, bg.border = NA)
+
+#--
+circos.clear()
+circos.par(gap.after = rep(c(rep(1, 4), 8), 3))
+
+chordDiagram(adjacency_list, annotationTrack = c("grid", "axis"),
+    preAllocateTracks = list(
+        track.height = uh(4, "mm"),
+        track.margin = c(uh(4, "mm"), 0)
+))
+
+circos.track(track.index = 2, panel.fun = function(x, y) {
+    sector.index = get.cell.meta.data("sector.index")
+    xlim = get.cell.meta.data("xlim")
+    ylim = get.cell.meta.data("ylim")
+    circos.text(mean(xlim), mean(ylim), sector.index, cex = 0.6, niceFacing = TRUE)
+}, bg.border = NA)
+
+highlight.sector(africa, track.index = 1, col = "red", 
+    text = "Africa", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(asia, track.index = 1, col = "green", 
+    text = "Asia", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(europe, track.index = 1, col = "blue", 
+    text = "Europe", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(north_america, track.index = 1, col = "orange", 
+    text = "North America", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(oceania, track.index = 1, col = "purple", 
+    text = "Oceania", cex = 0.8, text.col = "white", niceFacing = TRUE)
+
+highlight.sector(south_america, track.index = 1, col = "brown", 
+    text = "South America", cex = 0.8, text.col = "white", niceFacing = TRUE)
 

### 2019-05-06 code/paper.Rmd
stash

@@
 
-ip_regex <- "(?(?=.*?(\\d+\\.\\d+\\.\\d+\\.\\d+).*?)(\\1|))"
-
 get_ip_addresses <- function(x){
   re <- regexpr(
-  ip_regex, 
+  "(?(?=.*?(\\d+\\.\\d+\\.\\d+\\.\\d+).*?)(\\1|))", 
   x, perl = TRUE)
@@
 
-```
-
-Do WH sites have more geographically diverse contributions?
-
-Get locations for random pages.
-
-How many IP edits on each page?
-
-```{r}
-randoms_revision_history_page_details <- 
-  map_df(ten_k_random_wp_pages_lst, 
-         ~.x$revision_history_page_details, 
-         .id = "page")
-
-randoms_revision_history_page_details_ip <- 
-randoms_revision_history_page_details %>% 
-    mutate(is_ip_address = ifelse(get_ip_addresses(rh_user) != "", TRUE, FALSE),
-         page = as.numeric(page))
-
-randoms_revision_history_page_details_ip_prop <- 
-  randoms_revision_history_page_details_ip %>% 
-  group_by(page) %>% 
-  summarise(prop_ip_addresses = sum(is_ip_address) / n() )
-
-ggplot(randoms_revision_history_page_details_ip_prop,
-       aes(prop_ip_addresses)) +
-  geom_histogram() +
-  theme_minimal()
-```
-
-Overall location of IP edits for all random pages
-
-```{r}
-randoms_revision_history_page_details_ip_location <- 
-randoms_revision_history_page_details_ip %>% 
-  filter(is_ip_address) %>% 
-  mutate(ip_location = map(rh_user, ~maxmind(.x, ip_db)))  %>% 
-  unnest(ip_location)
-
-randoms_revision_history_page_details_ip_location_tally <- 
-randoms_revision_history_page_details_ip_location %>% 
-  filter(!is.na(country_name)) %>% 
-  mutate(country_name = fct_rev(fct_infreq(country_name))) %>% 
-  group_by(country_name) %>% 
-  tally(sort = TRUE) %>% 
-  filter(n > 100)
-
-ggplot(randoms_revision_history_page_details_ip_location_tally,
-       aes(country_name, n)) +
-  geom_col() +
-  coord_flip()   +
-  theme_minimal() +
-  scale_y_continuous(labels = scales::comma)
-```
-
-What's the geographic diversity of edits per random page?
-
-```{r}
-randoms_revision_history_page_details_ip_location_props_per_page <- 
-randoms_revision_history_page_details_ip_location %>% 
-  filter(!is.na(country_name)) %>% 
-  mutate(country_name = fct_rev(fct_infreq(country_name))) %>% 
-  group_by(page, country_name) %>% 
-  tally() %>% 
-  mutate(prop = n / sum(n)) %>% 
-  filter(country_name %in% randoms_revision_history_page_details_ip_location_tally$country_name)
-
-ggplot(randoms_revision_history_page_details_ip_location_props_per_page,
-       aes(country_name, 
-           prop)) +
-  geom_boxplot() +
-  coord_flip()
-
-randoms_revision_history_page_details_ip_location_props_per_page_div <- 
-  randoms_revision_history_page_details_ip_location_props_per_page %>% 
-  group_by(page) %>% 
-  summarise(shannon = vegan::diversity(n))
-
-ggplot(randoms_revision_history_page_details_ip_location_props_per_page_div,
-       aes( shannon)) +
-  geom_histogram() 
-```
-
-```{r}
-# analyse the countries of IP address vs country of WH site
 revision_history_page_details_ip_addresses <- 
@@
 
+# analyse the countries of IP address vs country of WH site
 revision_history_page_details_ip_addresses_df <- 
@@
     text = "South America", cex = 0.8, text.col = "white", niceFacing = TRUE)
+```
+
+```{r}
 
@@
 
-Look at distributions of variables, then say 2sd is extreme, and match those to the WH pages to find out what they are
-
-What's the typical distribution of talk page length?
-
-```{r}
-ten_k_random_wp_pages %>% 
-  mutate(tp_divided_by_page_word_count = talk_page_wordcount / page_wordcount) %>% 
-  ggplot(aes(talk_page_wordcount)) +
-  geom_histogram() +
-  scale_x_log10(labels = scales::comma_format(accuracy = 0.01))
-```
-
-Can we detect -ve sentiment on the talk pages? Perhaps as distributions, over every 100 words per page
-
-```{r}
-library(tidytext)
-
-```
-
-What's the typical distribution of the proportion of edits that are reverts?
-
-```{r}
-ggplot(ten_k_random_wp_pages,
-       aes(rh_revert_prop)) +
-  geom_histogram() +
-  scale_x_log10()
-
-```
-
-What are the keywords for controversy in edit messages? And how common are these warrning messages?
-
-```{r}
-randoms_revision_history_page_details_ip_warring_words <- 
-randoms_revision_history_page_details_ip %>% 
-  mutate(warring_words = (str_detect(rh_comment, 'undid|vandalism|why|inaccurate|wrong|warning|blocked|warring|disputed|neutral|unacceptable' )))
-
-# distribution of edits with warring words
-randoms_revision_history_page_details_ip_warring_words_prop <- 
-randoms_revision_history_page_details_ip_warring_words %>% 
-  group_by(page) %>% 
-  summarise(prop_warring_edits = sum(warring_words) / n())
-
-ggplot(randoms_revision_history_page_details_ip_warring_words_prop,
-         aes(prop_warring_edits)) +
-  geom_histogram() +
-  scale_x_log10()
-```
-
-Is there are correlation between the proportion of warring words and talk page length?
-
-```{r}
-# some interesting groupings
-randoms_revision_history_page_details_ip_warring_words_prop %>% 
-  left_join(ten_k_random_wp_pages %>% 
-  mutate(page = 1:nrow(.))) %>% 
-  filter(prop_warring_edits > 0) %>% 
-  ggplot(aes(prop_warring_edits, 
-             talk_page_wordcount ,
-             size = page_wordcount)) +
-  geom_point(alpha = 0.2)
-```
-
-Is there are correlation between the proportion of warring words and revert frequency?
-
-```{r}
-randoms_revision_history_page_details_ip_warring_words_prop_revert_prop <- 
-randoms_revision_history_page_details_ip_warring_words_prop %>% 
-  left_join(ten_k_random_wp_pages %>% 
-  mutate(page = 1:nrow(.))) %>% 
-  filter(prop_warring_edits != 0,
-         rh_revert_prop != 0)
-
-lm(rh_revert_prop ~ prop_warring_edits, 
-   data = randoms_revision_history_page_details_ip_warring_words_prop_revert_prop) %>% summary
-
-ggplot(randoms_revision_history_page_details_ip_warring_words_prop_revert_prop,
-         aes(prop_warring_edits, 
-             rh_revert_prop)) +
-  geom_point()
-```
-
 time between edits
-
-```{r}
-library(lubridate)
-randoms_revision_history_page_details_ip_time_diffs <- 
-randoms_revision_history_page_details_ip %>% 
-  group_nest(page) %>% 
-  mutate(time_diff = map(data, ~lag(.x$rh_date) - .x$rh_date)) %>% 
-  unnest(time_diff) %>% 
-  mutate(time_diff_days = as.numeric(time_diff / 60 / 60 / 24)) %>% 
-  mutate(time_diff_hours = as.numeric(time_diff / 60 / 60 )) %>% 
-  mutate(less_than_one_month = ifelse(time_diff_hours < 744, TRUE, FALSE)) %>% 
-  mutate(less_than_one_week = ifelse(time_diff_hours < 168, TRUE, FALSE)) %>% 
-  bind_cols(randoms_revision_history_page_details_ip)
-
-rle_tbl <- 
-tibble(lths = rle(randoms_revision_history_page_details_ip_time_diffs$rh_user)$lengths,
-vals = rle(randoms_revision_history_page_details_ip_time_diffs$rh_user)$values)
-
-rle_tbl2 <- tibble(
-  rh_user = rep(rle_tbl$vals, rle_tbl$lths),
-  lths2 = rep(rle_tbl$lths, rle_tbl$lths)
-)
-
-randoms_revision_history_page_details_ip_time_diffs %>% 
-  filter(!is.na(time_diff_hours)) %>% 
-  mutate(quick_three_edits = time_diff_hours + lag(time_diff_hours) + lag(time_diff_hours, 2) + lag(time_diff_hours, 3))
-
-randoms_revision_history_page_details_ip_time_diffs_quick <- 
-randoms_revision_history_page_details_ip_time_diffs %>% 
- nest(-page) %>%  
- mutate(edits_3 = map(data, ~.x %>% 
-                              filter(less_than_one_week) %>% 
-                              filter(n() > 4 ))) %>% 
-  unnest(edits_3)
-
-randoms_revision_history_page_details_ip_time_diffs %>% 
-  bind_cols(rle_tbl2) %>% 
-  filter(lths2 == 1) %>% 
-  filter(time_diff_hours < 24)
-
-ggplot(randoms_revision_history_page_details_ip_time_diffs,
-       aes(time_diff_days)) +
-  geom_histogram()
-
-```
-
-time series of edits: breakouts relating to events? monthly seems like a good level of aggregation. What can we do for spike detection?
-
-```{r}
-randoms_revision_history_page_details_ip_location %>% 
-  group_by(page) %>% 
-  mutate(the_d = floor_date(rh_date, "day")) %>% 
-    mutate(the_m = floor_date(rh_date, "month")) %>% 
-  group_by(page, the_m) %>% 
-  tally() %>% 
-  filter(n() > 130) %>%   # explore this value
-  ggplot() +
-  geom_line(aes(the_m,
-             n)) +
-  facet_wrap( ~ page, scales = "free")
-```
-
-Spike detection
-
-for randoms, what even is an anomaly?
-
-```{r}
-# devtools::install_github("hrbrmstr/AnomalyDetection")
-library(AnomalyDetection)
-randoms_revision_history_page_details_ip_location_monthly <- 
-randoms_revision_history_page_details_ip_location %>% 
-  group_by(page) %>% 
-  mutate(the_d = floor_date(rh_date, "day")) %>% 
-    mutate(the_m = floor_date(rh_date, "month")) %>% 
-  group_by(page, the_m) %>% 
-  tally() %>% 
-  filter(n() > 150) # explore this value
-
-randoms_revision_history_page_details_ip_location_monthly_anom <- 
-  randoms_revision_history_page_details_ip_location_monthly %>% 
-  ungroup %>% 
-  group_nest(page) %>% 
-  mutate(anomalies = map(data, ~ad_ts(.x, 
-                                      max_anoms = 0.2, 
-                                      alpha = 0.005,
-                                      threshold = "p95"))) %>% 
-  unnest(anomalies)
-
-ggplot() +
-  geom_line(
-    data=randoms_revision_history_page_details_ip_location_monthly %>% 
-      filter(page %in% randoms_revision_history_page_details_ip_location_monthly_anom$page), 
-    aes(the_m, n), 
-    size=0.125, color="lightslategray")  +
-  geom_point(
-    data=randoms_revision_history_page_details_ip_location_monthly_anom, 
-    aes(timestamp, anoms), 
-    color="#cb181d", alpha=1/3) +
-  scale_x_datetime(date_labels="%b\n%Y") +
-  facet_wrap( ~ page, scales = "free_y")
-
-```
-
-for WH sites
-
-```{r}
-revision_history_page_details_ip_addresses_df_monthly_edits <- 
-revision_history_page_details_ip_addresses_df  %>% 
-  mutate(the_d = floor_date(rh_date, "day")) %>% 
-    mutate(the_m = floor_date(rh_date, "month")) %>% 
-  group_by(Site, the_m) %>% 
-  tally() %>% 
-  filter(n() > 24) # explore this value
-
-# distribution of edits per month
-ggplot(revision_history_page_details_ip_addresses_df_monthly_edits,
-       aes(n)) +
-  geom_histogram() +
-  scale_x_log10()
-
-# subset so we get only sites with > 10 edits/month
-revision_history_page_details_ip_addresses_df_monthly_edits_10 <- 
-revision_history_page_details_ip_addresses_df_monthly_edits %>% 
-  filter(max(n) >= 10)
-
-```
-
-```{r}
-
-# detect anomalies
-revision_history_page_details_ip_addresses_df_monthly_edits_anoms <- 
-  revision_history_page_details_ip_addresses_df_monthly_edits_10 %>% 
-  ungroup %>% 
-  group_nest(Site) %>% 
-  mutate(anomalies = map(data, ~ad_ts(.x, 
-                                      max_anoms = 0.2, 
-                                      alpha = 0.005,
-                                      threshold = "p95"))) %>% 
-  unnest(anomalies) %>% 
-  group_by(Site) %>% 
-  filter(max(anoms) >= 50) # where the anomaly is 50 edits/month or more
-
-ggplot() +
-  geom_line(
-    data=revision_history_page_details_ip_addresses_df_monthly_edits_10 %>% 
-      filter(Site %in% revision_history_page_details_ip_addresses_df_monthly_edits_anoms$Site), 
-    aes(the_m, n), 
-    size=0.125, color="lightslategray")  +
-  geom_point(
-    data=revision_history_page_details_ip_addresses_df_monthly_edits_anoms, 
-    aes(timestamp, anoms), 
-    color="#cb181d", alpha=1/3) +
-  scale_x_datetime(date_labels="%b\n%Y") +
-  facet_wrap( ~ Site, scales = "free")
-```
+edit reverts
+talk page: length and sentiment
 

### 2019-05-08 code/paper.Rmd
making some figures

--- 2019-03-30 code/paper.Rmd
@@
   annotate("text", x = 30, y = 30, 
-           label = str_glue('Median = {median_number_unesco_sites_per_country} WH sites/country\nMode = {mode_number_unesco_sites_per_country} WH sites/country'),
+           label = str_glue('Median =\n{median_number_unesco_sites_per_country} WH sites/country\nMode =\n{mode_number_unesco_sites_per_country} WH sites/country'),
            size = 3) +
-  theme_nogrid(12)
+  theme_nogrid(8)
 
@@
     scale_fill_viridis_c(na.value="grey90") +
-  coord_sf() +
   coord_sf(ylim = c(-50, 90), datum = NA) +
-  theme_minimal()
+  theme_minimal() +
+  ggtitle("Cultural Sites on the UNESCO World Heritage list",
+          subtitle = "from https://whc.unesco.org/en/syndication")
 
@@
                     ymax=-70)
+
+ggsave("figures/wh_country_unesco_count_map.png")
 
@@
     scale_fill_viridis_c(na.value="grey90") +
-  coord_sf() +
   coord_sf(ylim = c(-50, 90), datum = NA) +
-  theme_minimal()
+  theme_minimal() +
+  ggtitle("Cultural Sites on the UNESCO World Heritage list with Wikipedia pages",
+          subtitle = str_glue("The top five are {wh_wk_country_counts %>% 
+                                                  arrange(-n) %>% 
+                                                  slice(1:5) %>% 
+                                                  pull(country) %>%
+                                                  str_flatten(collapse = ', ')}"))
 
@@
                     ymax=-70)
+
+ggsave("figures/wh_country_wikpedia_pages_count_map.png")
 ```
@@
     scale_fill_viridis_c(na.value="grey90") +
-  coord_sf() +
   coord_sf(ylim = c(-50, 90), datum = NA) +
-  theme_minimal()
+  theme_minimal() +
+  ggtitle("Ratio of number of Cultural Sites on the UNESCO World Heritage list\nto the number of those sites with Wikipedia pages")
 
@@
                     ymax=-70)
+
+ggsave("figures/wh_country_wikpedia_pages_ratio_map.png")
 ```
@@
 
+label_names <- list(
+  "page_wordcount"="Page word count",
+  "page_wikilinks_out_per_1k_words"="Number of wikilinks\nper 1k words",
+  "page_cited_items_on_per_1k_words"="Number of sources cited\nper 1k words"
+)
+
+labeller <- function(variable,value){
+  return(label_names[value])
+}
+
 # density plots
@@
   facet_wrap( ~ variable, 
-              scales = "free") +
-  theme_minimal()
+              scales = "free",
+              labeller = labeller) +
+  theme_minimal() +
+    ggtitle("Basic qualities about Wikipedia article content")
+
+  ggsave("figures/wh_wikpedia_pages_basic_content.png")
 ```
@@
 ```{r}
+library(ggrepel)
 ten_k_random_wp_pages_attent <- 
@@
          page_views_last_n_days_total)
+
+page_data_for_all_pages_attent_long <- 
+page_data_for_all_pages_attent %>% 
+  gather(variable, value) %>% 
+  bind_rows(ten_k_random_wp_pages_attent %>% 
+              gather(variable, value) %>% 
+              mutate(variable =  str_glue('rnd_{variable}'))) %>% 
+  mutate(source = ifelse(str_detect(variable, "rnd" ), "10k Random pages", 
+                         "World Heritage pages")) %>% 
+  mutate(variable = str_remove(variable, "rnd_"))
+
+# density plots
+  ggplot(page_data_for_all_pages_attent_long,
+         aes(value)) +
+  geom_density(aes(fill = source),
+               alpha = 0.3) +
+  scale_x_log10() +
+  scale_fill_viridis_d() +
+  facet_wrap( ~ variable, 
+              scales = "free") +
+  theme_minimal() +
+    ggtitle("Basic qualities about attention given to Wikipedia articles")
+
+ggsave("figures/wh_wikpedia_pages_attention_given.png")
+```
+
+```{r}
 
@@
 
-page_data_for_all_pages_attent_long <- 
-page_data_for_all_pages_attent %>% 
-  gather(variable, value) %>% 
-  bind_rows(ten_k_random_wp_pages_attent %>% 
-              gather(variable, value) %>% 
-              mutate(variable =  str_glue('rnd_{variable}'))) %>% 
-  mutate(source = ifelse(str_detect(variable, "rnd" ), "10k Random pages", 
-                         "World Heritage pages")) %>% 
-  mutate(variable = str_remove(variable, "rnd_"))
-
-# density plots
-  ggplot(page_data_for_all_pages_attent_long,
-         aes(value)) +
-  geom_density(aes(fill = source),
-               alpha = 0.3) +
-  scale_x_log10() +
-  scale_fill_viridis_d() +
-  facet_wrap( ~ variable, 
-              scales = "free") +
-  theme_minimal()
 ```

### 2019-05-08 code/paper.Rmd
stash

--- 2019-03-30 code/paper.Rmd
@@
 ```{r}
+
+n <- 12 # months of edit data
 revision_history_page_details_ip_addresses_df_monthly_edits <- 
@@
   tally() %>% 
-  filter(n() > 24) # explore this value
+  filter(n() >  n ) # n months worth of data - explore this value
 
@@
 
-# subset so we get only sites with > 10 edits/month
+# subset so we get only sites with > n1 edits/month, and at least 3 months worth of edits
+
+n1 <- 7  # edits per month
+n2 <- 20 # months worth of edits
 revision_history_page_details_ip_addresses_df_monthly_edits_10 <- 
 revision_history_page_details_ip_addresses_df_monthly_edits %>% 
-  filter(max(n) >= 10)
+  filter(max(n) >= n1) %>% 
+  group_by(Site) %>% 
+  filter(n() >= n2)
 
@@
   group_by(Site) %>% 
-  filter(max(anoms) >= 50) # where the anomaly is 50 edits/month or more
+  filter(max(anoms) >= 10) # where the anomaly is n edits/month or more
 
@@
 bots
+
+What do bots do?
+
+Do people undo bot actions often?
 

### 2019-05-08 code/paper.Rmd
edits per page

@@
 # density plots
+
+label_names <- list(
+  "page_wikilinks_in"="Number of wikilinks to the page",
+  "page_views_last_n_days_total"="Total page views\n(last 100 days)"
+)
+
+labeller <- function(variable,value){
+  return(label_names[value])
+}
+
   ggplot(page_data_for_all_pages_attent_long,
@@
   facet_wrap( ~ variable, 
-              scales = "free") +
+              scales = "free",
+              labeller = labeller) +
   theme_minimal() +
@@
 
-```{r}
-
+Scatterplot showing the WP sites that get the most attention
+
+```{r}
+library(ggrepel)
 page_data_for_all_pages %>% 
   select( Site,
+          page_wordcount,
          page_wikilinks_in, 
@@
              page_views_last_n_days_total,
-             label = Site)) +
-  geom_point(alpha = 0.4) +
+             label = str_wrap(Site, 30))) +
+  geom_point(alpha = 0.2,
+             aes(size = page_wordcount)) +
     geom_text_repel(
@@
     segment.size  = 0.2,
+    force = 50,
     segment.color = "grey50",
@@
   coord_fixed(0.5) +
-  theme_minimal()
-
+  theme_minimal(base_size = 14) +
+  labs(x = "Number of wikilinks to the page",
+       y = "Total page views (last 100 days)") +
+    ggtitle("Basic qualities about attention given to Wikipedia articles")
+
+ggsave("figures/wh_wikpedia_pages_attention_scatterplot.png")
 ```
@@
 number of edits, total, prop/words
+how many bot edits, how many reverts per page
 size of edits
-divesity of editors
-
-```{r}
+diversity of editors
+
+```{r}
+# wh sites on wp
 revision_history_page_details <- 
@@
 
-ggplot(revision_history_page_details,
-       aes(rh_n_edits)) +
-  geom_histogram()
-
+# random sites
+
+ten_k_random_wp_pages_revision_history_page_details <- 
+  map_df(ten_k_random_wp_pages_lst, 
+         ~.x$revision_history_page_details, 
+         .id = 'Site')
+
+# very slow!
+ten_k_random_wp_pages_revision_history_page_details_summary_tbl <- 
+  ten_k_random_wp_pages_revision_history_page_details %>% 
+  mutate(Site = as.numeric(Site)) %>% 
+  group_by(Site) %>% 
+  summarise(
+         rh_n_editors = n_distinct(rh_user),
+         rh_n_edits =   n(),
+         rh_n_bot_edits = sum(bot),
+         rh_n_reverts = sum(revert)) %>% 
+  mutate(rh_revert_prop = rh_n_reverts / rh_n_edits,
+         rh_bot_edits_prop = rh_n_bot_edits / rh_n_edits)
+
+# plot both samples, number of edits per page
+bind_rows(revision_history_page_details %>% 
+            select(Site, rh_n_edits) %>% 
+            mutate(Site = "wh"),
+          ten_k_random_wp_pages_revision_history_page_details_summary_tbl %>% 
+            select(Site, rh_n_edits) %>% 
+            mutate(Site = "rand")) %>% 
+  ggplot(aes(rh_n_edits,
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+  scale_x_log10() +
+  scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Number of edits per page",
+       fill = "Wikipedia pages") +
+  theme_minimal()
+
+ggsave("figures/wh_wikpedia_edits_per_page.png")
 ```

### 2019-05-08 code/paper.Rmd
consumption of articles

@@
 
-## Basic qualitites of attention paid to articles
+## Basic qualities of consumption of articles
 
@@
   theme_minimal() +
-    ggtitle("Basic qualities about attention given to Wikipedia articles")
-
-ggsave("figures/wh_wikpedia_pages_attention_given.png")
+    ggtitle("Basic qualities about consumption of Wikipedia articles")
+
+ggsave("figures/wh_wikpedia_pages_consumption.png")
 ```

### 2019-05-09 code/paper.Rmd
up to reverts

@@
   geom_point(alpha = 0.2,
-             aes(size = page_wordcount)) +
+             aes(size = page_wordcount,
+                 colour = page_wordcount)) +
     geom_text_repel(
@@
   coord_fixed(0.5) +
+  scale_color_viridis_c(name = "Wordcount", 
+                        labels = c(20000, 15000, 10000, 5000),
+                        breaks = c(20000, 15000, 10000, 5000)) +
+  scale_size_continuous(name = "Wordcount", 
+                        labels = c(20000, 15000, 10000, 5000),
+                        breaks = c(20000, 15000, 10000, 5000)) +
+   guides(color= guide_legend(), size=guide_legend()) +
   theme_minimal(base_size = 14) +
@@
        y = "Total page views (last 100 days)") +
-    ggtitle("Basic qualities about attention given to Wikipedia articles")
-
-ggsave("figures/wh_wikpedia_pages_attention_scatterplot.png")
+    ggtitle("Basic qualities about the consumption of Wikipedia articles")
+
+ggsave("figures/wh_wikpedia_pages_consumption_scatterplot.png")
 ```
@@
 
-number of edits, total, prop/words
+number of edits, total, edit density (prop/words), size of edits
 how many bot edits, how many reverts per page
-size of edits
 diversity of editors
@@
 ```
+
+Edits per 1k words, as a measure of edit density
+
+```{r}
+revision_history_page_details_wordcount <- 
+  revision_history_page_details %>% 
+  bind_cols(page_data_for_all_pages %>% select(page_wordcount)) %>% 
+  mutate(edits_per_1k_words = rh_n_edits / (page_wordcount / 1000))
+
+ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets <- 
+bind_cols(ten_k_random_wp_pages, 
+          ten_k_random_wp_pages_revision_history_page_details_summary_tbl) %>% 
+  mutate(edits_per_1k_words = rh_n_edits / (page_wordcount / 1000))
+
+bind_rows(revision_history_page_details_wordcount %>% 
+            select(Site, edits_per_1k_words) %>% 
+            mutate(Site = "wh"),
+          ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets %>% 
+            select(Site, edits_per_1k_words) %>% 
+            mutate(Site = "rand")) %>% 
+  ggplot(aes(edits_per_1k_words,
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+  #xlim(0, 100) +
+  scale_x_log10() +
+  scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Number of edits per 1k words per page",
+       fill = "Wikipedia pages") +
+  theme_minimal()
+
+ggsave("figures/wh_wikpedia_edits_density_page.png")
+```
+
+Size of edits, absolute and raw
+
+```{r}
+page_data_for_all_pages_rh_tbl <- 
+map_df(page_data_for_all_pages$page_info_t, 
+      ~.x$revision_history_page_details, .id = "Site")
+
+label_names <- list(
+  "mean_abs_diff"="Absolute edit sizes",
+  "mean_diff"="Raw edit sizes"
+)
+
+labeller <- function(variable,value){
+  return(label_names[value])
+}
+
+bind_rows(page_data_for_all_pages_rh_tbl %>% 
+            select(Site, rh_diff_size) %>% 
+            group_by(Site) %>% 
+            summarise(mean_diff = mean((rh_diff_size)),
+                      mean_abs_diff = mean(abs(rh_diff_size))) %>% 
+            mutate(Site = "wh"),
+          ten_k_random_wp_pages_revision_history_page_details %>% 
+            select(Site, rh_diff_size) %>% 
+              group_by(Site) %>% 
+            summarise(mean_diff = mean((rh_diff_size)),
+                      mean_abs_diff = mean(abs(rh_diff_size))) %>% 
+            mutate(Site = "rand")) %>% 
+  gather(variable, value, -Site) %>% 
+  ggplot(aes(value,
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+  #xlim(0, 100) +
+  scale_x_log10() +
+  scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Average size of edits per article (bytes)",
+       fill = "Wikipedia pages") +
+  facet_wrap( ~ variable, labeller = labeller) +
+  theme_minimal()
+
+ggsave("figures/wh_wikpedia_edit_sizes.png")
+```
+
+How many edits made by bots? Proportion of edits per page made by bots
+
+```{r}
+bind_rows(
+
+page_data_for_all_pages_rh_tbl %>% 
+  group_by(Site) %>% 
+  summarise( n_bot_edits = sum(bot),
+             n_edits = n()) %>% 
+  mutate(prop_bot_edits = n_bot_edits / n_edits,
+           Site = "wh"),
+
+ten_k_random_wp_pages_revision_history_page_details %>%  
+  group_by(Site) %>% 
+summarise( n_bot_edits = sum(bot),
+           n_edits = n()) %>% 
+  mutate(prop_bot_edits = n_bot_edits / n_edits,
+         Site = "rand")
+) %>%
+
+  ggplot(aes(prop_bot_edits,
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+  #xlim(0, 100) +
+  scale_x_log10() +
+  scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Proportion of edits made by bots per article",
+       fill = "Wikipedia pages") +
+  theme_minimal()
+
+ggsave("figures/wh_wikpedia_edit_sizes.png")
+```
+
+Which WH pages are most edited by bots?
+
+```{r}
+library(ggrepel)
+
+wh_bots <- 
+ tibble(revision_history_page_details = map(page_data_for_all_pages$page_info_t, 
+      ~.x$revision_history_page_details))  %>% 
+  mutate(Site = page_data_for_all_pages$Site) %>% 
+  mutate(n_bot_edits = map_dbl(revision_history_page_details, ~sum(.x$bot)),
+         n_edits = map_int(revision_history_page_details, ~nrow(.))) %>% 
+  mutate(prop_bot_edits = n_bot_edits / n_edits) %>% 
+  arrange(desc(prop_bot_edits))
+
+  ggplot(wh_bots, 
+         aes(n_bot_edits,
+             n_edits,
+             label = str_wrap(Site, 30))) +
+  geom_point(alpha = 0.2,
+             aes(size =   prop_bot_edits,
+                 colour = prop_bot_edits)) +
+    geom_text_repel(
+    data            = wh_bots %>%  
+                      filter(prop_bot_edits > 0.36),
+    segment.size  = 0.2,
+    force = 50,
+    segment.color = "grey50",
+    direction     = "both"
+  ) +
+  scale_y_log10() +
+  scale_x_log10() +
+  coord_fixed(0.5) +
+  scale_color_viridis_c(name = "Proportion of\nedits by bots", 
+                        labels = c(0, 0.1, 0.2, 0.3, 0.4),
+                        breaks = c(0, 0.1, 0.2, 0.3, 0.4)) +
+  scale_size_continuous(name = "Proportion of\nedits by bots", 
+                        labels = c(0, 0.1, 0.2, 0.3, 0.4),
+                        breaks = c(0, 0.1, 0.2, 0.3, 0.4)) +
+   guides(color= guide_legend(), size=guide_legend()) +
+  theme_minimal(base_size = 14) +
+  labs(x = "Number of edits by bots",
+       y = "Total number of edits") +
+    ggtitle("Bot activity on Wikipedia articles")
+
+ggsave("figures/wh_wikpedia_pages_bot_edits_scatterplot.png")
+```
+
+which bots are most active on WH pages vs random pages?
+Cydebot: category edits
+Smackbot: dates in templates
+ClueBot NG: vandalism
+
+```{r}
+bind_rows(
+page_data_for_all_pages_rh_tbl %>% 
+  filter(bot == 1) %>% 
+  group_by(rh_user) %>% 
+  tally(sort = TRUE) %>% 
+  slice(1:10) %>% 
+  mutate( Site = "World Heritage Sites"),
+
+ten_k_random_wp_pages_revision_history_page_details %>% 
+  filter(bot == 1) %>% 
+  group_by(rh_user) %>% 
+  tally(sort = TRUE) %>% 
+    slice(1:10) %>% 
+   mutate( Site = "Random pages")) %>%
+
+  ggplot(aes(reorder(rh_user, n),
+             n)) +
+  geom_col() +
+  theme_minimal() +
+  coord_flip() +
+  facet_wrap( ~ Site, scales = "free") +
+  xlab("")
+
+ggsave("figures/wh_wikpedia_what_bots.png")
+```
+
+So about vandalism? do WH sites get more than random ones?
+
+```{r}
+bind_rows(
+page_data_for_all_pages_rh_tbl %>% 
+  mutate(vandalism = ifelse(str_detect(rh_comment, "vandal"), 1, 0)) %>%
+  group_by(Site) %>% 
+  summarise( n_vandal_edits = sum(vandalism),
+             n_edits = n()) %>% 
+  mutate(prop_vandal_edits = n_vandal_edits / n_edits,
+           Site = "World Heritage Sites"),
+
+ten_k_random_wp_pages_revision_history_page_details %>% 
+  mutate(vandalism = ifelse(str_detect(rh_comment, "vandal"), 1, 0)) %>%
+  group_by(Site) %>% 
+  summarise( n_vandal_edits = sum(vandalism),
+             n_edits = n()) %>% 
+  mutate(prop_vandal_edits = n_vandal_edits / n_edits, 
+         Site = "Random pages")
+) %>%
+
+   ggplot(aes(prop_vandal_edits,
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+  scale_x_log10() +
+  scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Proportion of edits relating to vandalism per article",
+       fill = "Wikipedia pages") +
+  theme_minimal()
+
+ggsave("figures/wh_wikpedia_vandalism_edits.png")
+
+```
+
+Which WH pages have the most vandalism?
+
+```{r}
+
+vandal_edits <- 
+ tibble(revision_history_page_details = map(page_data_for_all_pages$page_info_t, 
+      ~.x$revision_history_page_details))  %>% 
+  mutate(Site = page_data_for_all_pages$Site) %>% 
+  mutate(n_vandal_edits = map_dbl(revision_history_page_details, 
+                                  ~sum(ifelse(str_detect(.x$rh_comment, "vandalism"), 1, 0))),
+         n_edits = map_int(revision_history_page_details, ~nrow(.))) %>% 
+  mutate(prop_vandal_edits = n_vandal_edits / n_edits) %>% 
+  arrange(desc(prop_vandal_edits))
+
+ggplot(vandal_edits, 
+         aes(n_vandal_edits,
+             n_edits,
+             label = str_wrap(Site, 30))) +
+  geom_point(alpha = 0.2,
+             aes(size =   prop_vandal_edits,
+                 colour = prop_vandal_edits)) +
+    geom_text_repel(
+    data            = vandal_edits %>%  
+                      filter(prop_vandal_edits > 0.055),
+    segment.size  = 0.2,
+    force = 50,
+    segment.color = "grey50",
+    direction     = "both"
+  ) +
+  scale_y_log10() +
+  scale_x_log10() +
+  coord_fixed(0.5) +
+  scale_color_viridis_c(name = "Proportion of\nedits about vandalism", 
+                        labels = c(0, 0.025, 0.05, 0.075),
+                        breaks = c(0, 0.025, 0.05, 0.075)) +
+  scale_size_continuous(name = "Proportion of\nedits about vandalism", 
+                        labels = c(0, 0.025, 0.05, 0.075),
+                        breaks = c(0, 0.025, 0.05, 0.075)) +
+   guides(color= guide_legend(), size=guide_legend()) +
+  theme_minimal(base_size = 14) +
+  labs(x = "Number of edits about vandalism",
+       y = "Total number of edits") +
+    ggtitle("Editing about vandalism on Wikipedia articles")
+
+ggsave("figures/wh_wikpedia_pages_vandal_edits_scatterplot.png")
+
+```
+
+Reverts
 

### 2019-05-09 code/paper.Rmd
talk pages

@@
 ```{r}
+bind_rows(
+
 ten_k_random_wp_pages %>% 
-  mutate(tp_divided_by_page_word_count = talk_page_wordcount / page_wordcount) %>% 
-  ggplot(aes(talk_page_wordcount)) +
-  geom_histogram() +
-  scale_x_log10(labels = scales::comma_format(accuracy = 0.01))
-```
+  select(talk_page_wordcount) %>% 
+  mutate(Site = "Random pages"),
+
+page_data_for_all_pages %>% 
+  select(talk_page_wordcount) %>% 
+  mutate(Site = "World Heritage pages")
+) %>%
+
+  ggplot(aes(talk_page_wordcount, 
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+   scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Talk page word count",
+       fill = "Wikipedia pages") +
+  theme_minimal() +
+  scale_x_log10(labels = scales::comma_format(accuracy = 1))
+
+ggsave("figures/wh_wikpedia_pages_talk_page_worcount.png")
+```
+
+which WH pages have the longest talk pages?
 

### 2019-05-10 code/paper.Rmd
talk page length

@@
 
+```{r}
+
+```
+
+What's the typical distribution of talk page length?
+
+```{r}
+bind_rows(
+
+ten_k_random_wp_pages %>% 
+  select(talk_page_wordcount) %>% 
+  mutate(Site = "Random pages"),
+
+page_data_for_all_pages %>% 
+  select(talk_page_wordcount) %>% 
+  mutate(Site = "World Heritage pages")
+) %>%
+
+  ggplot(aes(talk_page_wordcount, 
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+   scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Talk page word count",
+       fill = "Wikipedia pages") +
+  theme_minimal() +
+  scale_x_log10(labels = scales::comma_format(accuracy = 1))
+
+ggsave("figures/wh_wikpedia_pages_talk_page_worcount.png")
+```
+
+which WH pages have the longest talk pages?
+
+```{r}
+
+wh_pages_talk_page_length <- 
+left_join(page_data_for_all_pages,
+          revision_history_page_details_wordcount)
+
+ggplot(wh_pages_talk_page_length,
+         aes(rh_n_edits,
+             rh_revert_prop,
+             label = str_wrap(Site, 30))) +
+  geom_point(alpha = 0.5,
+             aes(size =   (talk_page_wordcount),
+                 colour = (talk_page_wordcount))) +
+    geom_text_repel(
+    data            = wh_pages_talk_page_length %>%  
+                      filter(talk_page_wordcount > 8000),
+    segment.size  = 0.2,
+    colour = "black",
+    force = 50,
+    segment.color = "grey50",
+    direction     = "both"
+  ) +
+  scale_y_log10() +
+  scale_x_log10() +
+  coord_fixed(1) +
+  scale_color_viridis_c(name = "Talk page word count", 
+                        labels = c(5000, 10000, 15000, 20000),
+                        breaks = c(5000, 10000, 15000, 20000)) +
+  scale_size_continuous(name = "Talk page word count", 
+                        labels = c(5000, 10000, 15000, 20000),
+                        breaks = c(5000, 10000, 15000, 20000)) +
+   guides(color= guide_legend(), size=guide_legend()) +
+  theme_minimal(base_size = 14) +
+  labs(x = "Number of edits",
+       y = "Proportion of edits that are reverts") +
+    ggtitle("")
+
+ggsave("figures/wh_wikpedia_pages_talk_page_wordcount_reverts_scatterplot.png")
+
+```
+
 ## Locality
@@
 
-What's the typical distribution of talk page length?
-
-```{r}
-bind_rows(
-
-ten_k_random_wp_pages %>% 
-  select(talk_page_wordcount) %>% 
-  mutate(Site = "Random pages"),
-
-page_data_for_all_pages %>% 
-  select(talk_page_wordcount) %>% 
-  mutate(Site = "World Heritage pages")
-) %>%
-
-  ggplot(aes(talk_page_wordcount, 
-             fill = Site)) +
-  geom_density(alpha = 0.3) +
-   scale_fill_viridis_d(labels = c("Random", 
-                               "World Heritage")) +
-  labs(x = "Talk page word count",
-       fill = "Wikipedia pages") +
-  theme_minimal() +
-  scale_x_log10(labels = scales::comma_format(accuracy = 1))
-
-ggsave("figures/wh_wikpedia_pages_talk_page_worcount.png")
-```
-
-which WH pages have the longest talk pages?
+```{r}
+```
 

### 2019-05-11 code/paper.Rmd
diff in years between start of article and inscription year

--- 2019-05-09 code/paper.Rmd
@@
 
-## Basic qualities of the WP articles about WH sites
+## Basic qualities of the content of WP articles about WH sites
 
@@
 
-## Basic qualities of consumption of articles
+## Basic qualities of the consumption of WP articles about WH sites
 
@@
 
-## Basic qualities of the editing process
+## Basic qualities of the editing process of WP articles about WH sites
 
@@
 
+```{r}
+
+bind_rows(
+page_data_for_all_pages_rh_tbl %>% 
+  mutate(revert = ifelse(revert, 1, 0)) %>%
+  group_by(Site) %>% 
+  summarise( n_revert_edits = sum(revert),
+             n_edits = n()) %>% 
+  mutate(prop_revert_edits = n_revert_edits / n_edits,
+           Site = "World Heritage Sites"),
+
+ten_k_random_wp_pages_revision_history_page_details %>% 
+  mutate(revert = ifelse(revert, 1, 0)) %>%
+  group_by(Site) %>% 
+  summarise( n_revert_edits = sum(revert),
+             n_edits = n()) %>% 
+  mutate(prop_revert_edits = n_revert_edits / n_edits, 
+         Site = "Random pages")
+) %>%
+
+   ggplot(aes(prop_revert_edits,
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+  scale_x_log10() +
+  scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Proportion of reverting edits per article",
+       fill = "Wikipedia pages") +
+  theme_minimal()
+
+```
+
+What's the typical distribution of talk page length?
+
+```{r}
+bind_rows(
+
+ten_k_random_wp_pages %>% 
+  select(talk_page_wordcount) %>% 
+  mutate(Site = "Random pages"),
+
+page_data_for_all_pages %>% 
+  select(talk_page_wordcount) %>% 
+  mutate(Site = "World Heritage pages")
+) %>%
+
+  ggplot(aes(talk_page_wordcount, 
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+   scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Talk page word count",
+       fill = "Wikipedia pages") +
+  theme_minimal() +
+  scale_x_log10(labels = scales::comma_format(accuracy = 1))
+
+ggsave("figures/wh_wikpedia_pages_talk_page_worcount.png")
+```
+
+which WH pages have the longest talk pages?
+
+```{r}
+
+wh_pages_talk_page_length <- 
+left_join(page_data_for_all_pages,
+          revision_history_page_details_wordcount)
+
+ggplot(wh_pages_talk_page_length,
+         aes(rh_n_edits,
+             rh_revert_prop,
+             label = str_wrap(Site, 30))) +
+  geom_point(alpha = 0.5,
+             aes(size =   (talk_page_wordcount),
+                 colour = (talk_page_wordcount))) +
+    geom_text_repel(
+    data            = wh_pages_talk_page_length %>%  
+                      filter(talk_page_wordcount > 8000),
+    segment.size  = 0.2,
+    colour = "black",
+    force = 50,
+    segment.color = "grey50",
+    direction     = "both"
+  ) +
+  scale_y_log10() +
+  scale_x_log10(labels = scales::comma_format(accuracy = 1)) +
+  coord_fixed(1) +
+  scale_color_viridis_c(name = "Talk page word count", 
+                        labels = c(5000, 10000, 15000, 20000),
+                        breaks = c(5000, 10000, 15000, 20000)) +
+  scale_size_continuous(name = "Talk page word count", 
+                        labels = c(5000, 10000, 15000, 20000),
+                        breaks = c(5000, 10000, 15000, 20000)) +
+   guides(color= guide_legend(), size=guide_legend()) +
+  theme_minimal(base_size = 14) +
+  labs(x = "Number of edits",
+       y = "Proportion of edits that are reverts") +
+    ggtitle("")
+
+ggsave("figures/wh_wikpedia_pages_talk_page_wordcount_reverts_scatterplot.png")
+
+```
+
+Talk page topic modelling
+
+```{r}
+
+```
+
 ## Locality
@@
 
-What are the keywords for controversy in edit messages? And how common are these warrning messages?
+What are the keywords for controversy in edit messages? And how common are these warring messages?
 
@@
   geom_histogram()
+
+```
+
+## Temporal patterns
+
+Page ages: are WH pages younger than the typical WP page? What's their relationship to their inscription year?
+
+```{r}
+# get first and last edit, and inscription year
+library(lubridate)
+page_data_for_all_pages_rh_tbl_edit_start_end_span <- 
+page_data_for_all_pages_rh_tbl %>% 
+  group_by(Site) %>% 
+  summarise(first_edit_date = min(rh_date),
+            last_edit_date = max(rh_date),
+            edit_span = last_edit_date - first_edit_date) %>% 
+  mutate(Site = as.numeric(Site)) %>% 
+  arrange(Site) %>% 
+  bind_cols(page_data_for_all_pages) %>% 
+  mutate(inscription_year = as.Date(ISOdate(Year_num, 1, 1))) %>% 
+  mutate(diff_first_edit_inscription_year = as.numeric(ymd_hms(first_edit_date) - as.POSIXlt(inscription_year)) / 365 )
+
+ggplot(page_data_for_all_pages_rh_tbl_edit_start_end_span, 
+       aes(diff_first_edit_inscription_year)) +
+  geom_histogram() +
+  theme_minimal(base_size = 12)  +
+  geom_vline(xintercept = 0, colour = "red") +
+  ylim(0, 60) +
+  annotate("text", x = -10, y = 55, label = "Page appeared\nbefore inscription\n←", size = 10) +
+  annotate("text", x = 10,  y = 55, label = "Page appeared\nafter inscription\n→", size = 10)
 

### 2019-05-11 code/000-scrape-wikipedia.R
diff in years between start of article and inscription year

@@ -18,8 +18,8 @@ n_and_c_asia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_N
 w_asia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Western_Asia"
 e_asia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_sites_in_Eastern_Asia"
 s_asia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_sites_in_Southern_Asia"
-# SE Asia list currently removed due to copyvio :(
-se_asia <- "https://en.wikipedia.org/w/index.php?title=List_of_World_Heritage_Sites_in_Southeast_Asia&direction=prev&oldid=878049179"
+se_asia <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Southeast_Asia"
+# # SE Asia list currently removed due to copyvio :( "https://en.wikipedia.org/w/index.php?title=List_of_World_Heritage_Sites_in_Southeast_Asia&direction=prev&oldid=878049179"
 
 # Europe
 n_europe <- "https://en.wikipedia.org/wiki/List_of_World_Heritage_Sites_in_Northern_Europe"
@@ -75,8 +75,8 @@ which_table_has_the_sites <-
 } else {
   
   # the SE Asia table is troublesome 
-  region_table_xml <- region_table_xml_all_tables[3]
-  region_table_xml_table <- html_table(region_table_xml)[[1]]
+  region_table_xml <- region_table_xml_all_tables[2]
+  region_table_xml_table <- html_table(region_table_xml, fill = TRUE)[[1]]
 }
   
   # filter so we only keep the cultural sites
@@ -148,8 +148,6 @@ tbl_n_and_c_asia  <-  map_df(n_and_c_asia,   get_table_of_sites_per_region)
 tbl_w_asia  <-        map_df(w_asia ,   get_table_of_sites_per_region) 
 tbl_e_asia  <-        map_df(e_asia ,   get_table_of_sites_per_region) 
 tbl_s_asia  <-        map_df(s_asia ,   get_table_of_sites_per_region) 
-
-# special handling needed
 tbl_se_asia  <-       map_df(se_asia ,   get_table_of_sites_per_region) 
 
 tbl_n_europe <-       map_df(n_europe,   get_table_of_sites_per_region) 
@@ -220,31 +218,6 @@ country_site_page_ratio <-
          total = no_page + has_page) %>% 
[…]

### 2019-05-11 code/paper.Rmd
page ages

@@
 }
+```
+
+## Some sort of clustering
+
+```{r}
+normalize = function(x) (x-min(x))/(max(x)-min(x))
+
+#--------------------------------------------------------------------------
+# take a look at the distribution of page variables
+some_page_variables <- 
+  page_data_for_all_pages %>% 
+  select(page_wordcount, 
+         page_wikilinks_out,
+         page_wikilinks_in,
+         page_cited_items_on) %>% 
+  mutate(page_wikilinks_out_per_word = page_wikilinks_out / page_wordcount,
+         page_cited_items_on_per_word = page_cited_items_on / page_wordcount)
+
+# umap
+library(uwot)
+library("tmap")
+data("World")
+
+pages_umap_input <- 
+  some_page_variables  %>% 
+  mutate(page_wordcount_norm = normalize(page_wordcount),
+         page_wikilinks_in_norm= normalize(page_wikilinks_in),
+         page_wikilinks_out_per_word_norm = normalize(page_wikilinks_out_per_word),
+         page_cited_items_on_per_word_norm = normalize(page_cited_items_on_per_word)) %>% 
+  select(-page_wordcount,
+         -page_cited_items_on, 
+         -page_wikilinks_out,
+         -page_wikilinks_in,
+         -page_wikilinks_out_per_word,
+         -page_cited_items_on_per_word) %>% 
+  bind_cols(., page_data_for_all_pages[ , 'country'] ) %>% 
+  filter_all(all_vars(!is.na(.))) %>% 
+  left_join(World %>% 
+              select(name, continent), 
+            by = c('country' = 'name'))
+
+# compute umap
+
+pages_umap_input_selected <- 
+  pages_umap_input %>% 
+  select(-country, 
+         -continent,
+         -geometry
+         )
+
+pages_umap_output <- 
+  pages_umap_input_selected %>% 
+  umap(., 
+       n_neighbors = 60, 
+       min_dist = 0.7,
+       nn_method = "annoy",
+       init = "spca") %>% 
+  as_tibble()
+
+# compute hdbscan clusters
+library(dbscan)
+hdbscan_out <- hdbscan(pages_umap_output, 
+                       minPts = 5)
+
+table(hdbscan_out$cluster)
+
+main_plot <- 
+ggplot(pages_umap_output,
+       aes(V1, V2)) +
+  geom_point(
+    aes(colour = factor(hdbscan_out$cluster),
+        size =  pages_umap_input_selected$page_wordcount_norm  ,
+        shape = pages_umap_input$continent
+        )) +
+  scale_size(range = c(2,7), guide = FALSE) +
+  scale_shape(name = "Continent") +
+  scale_color_viridis_d(guide = FALSE) +
+  theme_minimal() +
+  theme(legend.position = c(0.1, 0.8)) +
+  xlab("") +
+  ylab("")
+
+# train a feature-selecting classificator like random forests on 
+# the cluster labels
+
+rand_forest_input <- 
+  pages_umap_input_selected %>% 
+  mutate(clus = hdbscan_out$cluster) %>% 
+  filter(clus != 0)
+
+library(caret)
+
+fit <- train(
+  clus ~ .,
+  data = rand_forest_input,
+  method = "ranger",
+  trControl = trainControl(method="cv", 
+                            number = 10, 
+                            allowParallel = TRUE, 
+                            verbose = TRUE),
+  importance = 'permutation')
+
+fit
+var_imp_tbl <- tibble(var = row.names(varImp(fit)$importance),
+                      imp = varImp(fit)$importance$Overall)
+
+theme_nogrid <- function (base_size = 12, base_family = "") {
+  theme_bw(base_size = base_size, 
+           base_family = base_family) %+replace% 
+    theme(panel.grid = element_blank() )   
+}
+
+sub_plot <- 
+ggplot(var_imp_tbl,
+       aes(reorder( var, -imp ),
+           imp)) +
+  geom_col() +
+  coord_flip() +
+  xlab("") +
+  ylab("") +
+  theme_nogrid(base_size = 6)
+
+# plot plus subplot
+main_plot + 
+  annotation_custom(ggplotGrob(sub_plot), 
+                    xmin = 3, 
+                    xmax = 6, 
+                    ymin= 6.5, 
+                    ymax= 3.5)
+
+ggsave("figures/wh_country_umap_hdbscan.png")
 ```
@@
 
-## Locality
+## Spatial patterns
 
@@
 
-ggplot(randoms_revision_history_page_details_ip_prop,
-       aes(prop_ip_addresses)) +
-  geom_histogram() +
-  theme_minimal()
+both_ip_props <- 
+bind_rows(
+revision_history_page_details_ip_addresses_countries %>% 
+  ungroup %>% 
+  select(prop_anon_of_all_edits) %>% 
+  mutate(source = "World Heritage Sites", 
+         prop_ip_addresses = prop_anon_of_all_edits),
+
+randoms_revision_history_page_details_ip_prop %>% 
+    ungroup %>% 
+  select(prop_ip_addresses) %>% 
+    mutate(source = "Random pages"))
+
+ggplot(both_ip_props,
+       aes(fill = source, 
+           prop_ip_addresses)) +
+  geom_density(alpha = 0.3) +
+   scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  theme_minimal() +
+  xlab("Proportion of all edits that are anonymous")
+
+ggsave("figures/proportion_of_IP_edits.png")
 ```
@@
   geom_histogram() +
-  theme_minimal()
+  theme_minimal(base_size = 12) +
+  xlab("Proportion of all edits that are anonymous")
 ```
@@
 
+```
+
+```{r}
+
+# stuff that doesn't work
+
 highlight.sector(africa, track.index = 1, col = "#00FF0040", 
@@
     text = "South America", cex = 0.8, text.col = "white", niceFacing = TRUE)
-```
-
-```{r}
 
@@
   mutate(inscription_year = as.Date(ISOdate(Year_num, 1, 1))) %>% 
-  mutate(diff_first_edit_inscription_year = as.numeric(ymd_hms(first_edit_date) - as.POSIXlt(inscription_year)) / 365 )
+  mutate(diff_first_edit_inscription_year = as.numeric( as.POSIXlt(inscription_year) - ymd_hms(first_edit_date) ) / 365 )
+
+page_data_for_random_rh_tbl_edit_start_end_span <- 
+randoms_revision_history_page_details %>% 
+  group_by(page) %>% 
+  summarise(first_edit_date = min(rh_date),
+            last_edit_date = max(rh_date),
+            edit_span = last_edit_date - first_edit_date) %>% 
+  mutate(page = as.numeric(page)) %>% 
+  arrange(page)
+
+bind_rows(
+
+  page_data_for_all_pages_rh_tbl_edit_start_end_span %>% 
+    select(edit_span) %>% 
+    mutate(source = "World Heritage"),
+
+  page_data_for_random_rh_tbl_edit_start_end_span %>% 
+     select(edit_span) %>% 
+    mutate(source = "Random")
+
+) %>% 
+  ggplot() +
+geom_density(aes(as.numeric(edit_span), 
+                 fill = source),
+                 alpha = 0.3) +
+  # scale_x_log10() +
+  scale_fill_viridis_d() +  
+  theme_minimal(base_size = 12) + 
+  xlab("Age of Wikipedia page (days)")
+
+ggsave("figures/wh_wikpedia_pages_ages.png")
+
+```
+
+Time between inscription year and first edit
+
+```{r}
+
+ggplot(page_data_for_all_pages_rh_tbl_edit_start_end_span,
+       aes(Year_num, 
+           diff_first_edit_inscription_year)) +
+  geom_jitter(alpha =  0.1, size = 3)  +
+  geom_vline(xintercept = 2001, colour = "red") +
+  geom_hline(yintercept = 0, colour = "red") +
+  theme_minimal(base_size = 12) + 
+  xlab("Year of inscription on World Heritage list") +
+  ylab("Difference between year of\ninscriptionand first edit on Wikipedia")
+
+ggplot(page_data_for_all_pages_rh_tbl_edit_start_end_span,
+       aes(Year_num, 
+           first_edit_date)) +
+  geom_jitter(alpha =  0.1, size = 3) +
+  theme_minimal(base_size = 12) + 
+  xlab("Year of inscription on World Heritage list") +
+  ylab("first edit on Wikipedia")
+
+ggplot(page_data_for_all_pages_rh_tbl_edit_start_end_span,
+       aes(Year_num)) +
+  geom_histogram() + 
+  theme_minimal(base_size = 12) +
+  scale_x_continuous(breaks = seq(1975, 2019, 1)) +
+  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
+  xlab("Year of inscription on World Heritage list")
+
+ggsave("figures/wh_wikpedia_pages_inscription_year_hist.png")
 
@@
   theme_minimal(base_size = 12)  +
-  geom_vline(xintercept = 0, colour = "red") +
-  ylim(0, 60) +
-  annotate("text", x = -10, y = 55, label = "Page appeared\nbefore inscription\n←", size = 10) +
-  annotate("text", x = 10,  y = 55, label = "Page appeared\nafter inscription\n→", size = 10)
+  geom_segment(x = 0, xend = 0, y = 0, yend = 50, colour = "red") +
+   geom_segment(x = -10, xend = -10, y = 0, yend = 50, colour = "blue") +
+   geom_segment(x = -22, xend = -22, y = 0, yend = 50, colour = "blue") +
+  ylim(0, 70) +
+  annotate("text", x = 10, y = 59, label = "Page appeared\nbefore inscription\n→", size =8) +
+  annotate("text", x =-10,  y = 59, label = "Page appeared\nafter inscription\n←", size = 8) +
+  annotate("text", x =-22,  y = 5, label = "Inscribed in 1983→", 
+           size = 3, colour = "white", hjust = 1  ) +
+  annotate("text", x =-10,  y = 5, label = "Inscribed in 1994→", 
+           size = 3, colour = "white", hjust = 1 ) +
+  annotate("text", x =0,  y = 5, label = "Inscribed in 2001→", 
+           size = 3, colour = "white", hjust = 1 ) +
+  xlab("Difference between year of inscription on World Heritage list and first edit on Wikipedia")
+
+ggsave("figures/wh_wikpedia_pages_diff_time_inscription.png")
 
@@
   facet_wrap( ~ page, scales = "free")
+
 ```
@@
 ```
-
-## Technicity
-
-bots
-
-What do bots do?
-
-Do people undo bot actions often?
 

### 2019-05-11 code/000-scrape-wikipedia.R

@@ -490,7 +490,28 @@ page_data_for_all_pages_result <- page_data_for_all_pages$result
 saveRDS(page_data_for_all_pages_result, 
         '../data/page_data_for_all_pages.rds')
 
+# get talk page content
 
+get_talk_page_content <- function(x){
+  if(x == "https://en.wikipedia.orgNA"){
+  content <- ""
+} else {
+  content <-
+    x %>% 
+    read_html() %>% 
+    html_nodes("#ca-talk a") %>% 
+    html_attr('href') %>% 
+    str_glue("https://en.wikipedia.org",.) %>% 
+    read_html() %>% 
+    html_nodes("#content") %>% 
+    html_text() 
+}
+return(content)
+}
+
+wh_wiki_table_talk_page_content <- 
+  map(wh_wiki_table$site_page_link, 
+      ~get_talk_page_content(.x))
 
 
 

### 2019-05-11 code/001-EDA.R

@@ -85,7 +85,8 @@ ggplot(pages_umap_output,
   geom_point(
     aes(colour = factor(hdbscan_out$cluster),
         size =  pages_umap_input_selected$page_wordcount_norm  ,
-        shape = pages_umap_input_rh$continent)) +
+        shape = pages_umap_input$continent
+        )) +
   scale_size(range = c(2,7), guide = FALSE) +
   scale_shape(name = "Continent") +
   scale_color_viridis_d(guide = FALSE) +
@@ -139,10 +140,10 @@ ggplot(var_imp_tbl,
 # plot plus subplot
 main_plot + 
   annotation_custom(ggplotGrob(sub_plot), 
-                    xmin = -10.0, 
-                    xmax = -2, 
-                    ymin=-7.5, 
-                    ymax=-3.5) 
+                    xmin = 3, 
+                    xmax = 6, 
+                    ymin= 6.5, 
+                    ymax= 3.5) 
 
 
 

### 2019-05-11 code/000-scrape-wikipedia.R
stash

@@ -513,6 +513,10 @@ wh_wiki_table_talk_page_content <-
   map(wh_wiki_table$site_page_link, 
       ~get_talk_page_content(.x))
 
+# save it
+saveRDS(wh_wiki_table_talk_page_content, 
+        '../data/wh_wiki_table_talk_page_content.rds')
+
 
 
 

### 2019-05-11 code/paper.Rmd
stash
trying to do topic modelling

@@
                       "wh_wiki_table.csv"))
+
+# the talk pages for all WH sites, with WP pages (n = 846)
+wh_wiki_talk_pages <-  readRDS(here::here("data", 
+                     "wh_wiki_table_talk_page_content.rds"))
 
@@
 
+Which articles have the most reverts?
+
+```{r}
+
+```
+
 What's the typical distribution of talk page length?
@@
 ```{r}
-
+library(tidytext)
+
+tidy_talk <- 
+enframe(unlist(wh_wiki_talk_pages)) %>% 
+  mutate(clean_text = str_remove_all(value, "\n|\t")) %>% 
+  unnest_tokens(word, clean_text) %>% 
+  anti_join(stop_words) %>% 
+  filter(!word %in% c("article", "page", "talk", "utc", "class", "edit", "project's"))
+
+# top words
+tidy_talk %>% 
+  count(word, sort = TRUE)
+
+# biggest documents
+tidy_talk %>% 
+  group_by(name) %>% 
+  tally(sort = TRUE)
+```
+
+The statistic tf-idf identifies words that are important to a document in a collection of documents; in this case, we’ll see which words are important in one of the talk pages compared to the others.
+
+```{r eval = FALSE}
+
+library(drlib) # devtools::install_github("dgrtwo/drlib")
+
+tidy_talk_tf_idf <- tidy_talk %>%
+  count(name, word, sort = TRUE) %>%
+  bind_tf_idf(word, name, n) %>%
+  arrange(-tf_idf) %>%
+  group_by(name) %>%
+  top_n(10) %>%
+  ungroup
+
+tidy_talk_tf_idf %>%
+  mutate(word = reorder_within(word, tf_idf, name)) %>%
+  ggplot(aes(word, tf_idf, fill = name)) +
+  geom_col(alpha = 0.8, show.legend = FALSE) +
+  facet_wrap(~ name, scales = "free", ncol = 3) +
+  scale_x_reordered() +
+  coord_flip() +
+  theme(strip.text=element_text(size=11)) +
+  labs(x = NULL, y = "tf-idf",
+       title = "Highest tf-idf words in talk pages ",
+       subtitle = "")
 ```

### 2019-05-12 code/paper.Rmd
topic model network

--- 2019-05-11 code/paper.Rmd
@@
 
+Number of unique editors per page
+
+```{r}
+# plot both samples, number of edits per page
+bind_rows(revision_history_page_details %>% 
+            select(Site, rh_n_editors) %>% 
+            mutate(Site = "wh"),
+          ten_k_random_wp_pages_revision_history_page_details_summary_tbl %>% 
+            select(Site, rh_n_editors) %>% 
+            mutate(Site = "rand")) %>% 
+  ggplot(aes(rh_n_editors,
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+  scale_x_log10(labels = scales::comma_format(accuracy = 1)) +
+  scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Number of editors per page",
+       fill = "Wikipedia pages") +
+  theme_minimal()
+
+ggsave("figures/wh_wikpedia_editors_per_page.png")
+```
+
+Number of unique editors per 1k words per page
+
+```{r}
+revision_history_page_details_wordcount <- 
+  revision_history_page_details %>% 
+  bind_cols(page_data_for_all_pages %>% select(page_wordcount)) %>% 
+  mutate(editors_per_1k_words = rh_n_editors / (page_wordcount / 1000))
+
+ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets <- 
+bind_cols(ten_k_random_wp_pages, 
+          ten_k_random_wp_pages_revision_history_page_details_summary_tbl) %>% 
+  mutate(editors_per_1k_words = rh_n_editors / (page_wordcount / 1000))
+
+bind_rows(revision_history_page_details_wordcount %>% 
+            select(Site, editors_per_1k_words) %>% 
+            mutate(Site = "wh"),
+          ten_k_random_wp_pages_revision_history_page_details_summary_tbl_all_dets %>% 
+            select(Site, editors_per_1k_words) %>% 
+            mutate(Site = "rand")) %>% 
+  ggplot(aes(editors_per_1k_words,
+             fill = Site)) +
+  geom_density(alpha = 0.3) +
+  scale_x_log10(labels = scales::comma_format(accuracy = 1)) +
+  scale_fill_viridis_d(labels = c("Random", 
+                               "World Heritage")) +
+  labs(x = "Number of editors per 1k words per page",
+       fill = "Wikipedia pages") +
+  theme_minimal()
+
+ggsave("figures/wh_wikpedia_editors_density_page.png")
+```
+
 Size of edits, absolute and raw
@@
 
-ggsave("figures/wh_wikpedia_edit_sizes.png")
+ggsave("figures/wh_wikpedia_edits_by_bots.png")
 ```
@@
     data            = vandal_edits %>%  
-                      filter(prop_vandal_edits > 0.055),
+                      filter(prop_vandal_edits > 0.05),
     segment.size  = 0.2,
@@
   theme_minimal()
+
+ggsave("figures/wh_wikpedia_pages_revert_edits.png")
+
+```
+
+Which articles have the most reverts?
+
+```{r}
+
+ggplot(revision_history_page_details, 
+         aes(rh_user_bot_prop,
+             rh_n_edits,
+             label = str_wrap(Site, 15))) +
+  geom_point(alpha = 0.2,
+             aes(size =   rh_revert_prop,
+                 colour = rh_revert_prop)) +
+    geom_text_repel(
+    data            = revision_history_page_details %>%  
+                      filter(rh_revert_prop > 0.12),
+    segment.size  = 0.2,
+    force = 50,
+    segment.color = "grey50",
+    direction     = "both"
+  ) +
+  scale_y_log10() +
+  scale_x_log10() +
+  coord_fixed(0.5) +
+  scale_color_viridis_c(name = "Proportion of\n edits reverted", 
+                        labels = c(0, 0.04, 0.08, 0.12, 0.16),
+                        breaks = c(0, 0.04, 0.08, 0.12, 0.16)) +
+  scale_size_continuous(name = "Proportion of\n edits reverted", 
+                        labels = c(0, 0.04, 0.08, 0.12, 0.16),
+                        breaks = c(0, 0.04, 0.08, 0.12, 0.16)) +
+   guides(color= guide_legend(), size=guide_legend()) +
+  theme_minimal(base_size = 12) +
+  labs(x = "Proportion of bots",
+       y = "Total number of edits") +
+    ggtitle("Reverted edits on Wikipedia articles")
+
+ggsave("figures/wh_wikpedia_pages_reverts_edits_scatterplot.png")
+```
+
+Is there a correlation between reverts and vandalism?
+
+```{r}
+left_join(page_data_for_all_pages, vandal_edits) %>% 
+  ggplot(aes(rh_revert_prop, 
+             prop_vandal_edits,
+             size = n_edits)) +
+  geom_point() +
+  theme_minimal(base_size = 12) +
+  labs(x = "Proportion of edits reverted",
+       y = "Proportion of edits responding to vandalism") +
+    coord_fixed(1)
+
+ggsave("figures/wh_wikpedia_pages_reverts_vandal_edits_scatterplot.png")
 
@@
 ```{r}
-
+library(tidytext)
+
+tidy_talk <- 
+enframe(unlist(wh_wiki_talk_pages)) %>% 
+  mutate(clean_text = str_remove_all(value, "\n|\t")) %>% 
+  unnest_tokens(word, clean_text) %>% 
+  anti_join(stop_words) %>% 
+  filter(!word %in% c("article", "page", "talk", "utc", 
+                      "class", "edit", "project's",
+                      "importance", "rated", "wikiproject",
+                      "project", "article", "articles", "article's",
+                      "wikipedia", "start", "scale", 
+                      "world", "heritage", "sites",
+                      "links", "http", "parser", 
+                      "output", "mw", "https",
+                      "unsigned", "comment")) %>% 
+  filter(!str_detect(word, "[[:digit:]]+")) %>% 
+  filter(!str_detect(word, ":")) %>% 
+  filter(!str_detect(word, "articles")) %>% 
+  filter(!str_detect(word, "jump")) %>% 
+  filter(!str_detect(word, "\\."))
+
+# top words
+tidy_talk %>% 
+  count(word, sort = TRUE)
+
+# biggest documents
+tidy_talk %>% 
+  group_by(name) %>% 
+  tally(sort = TRUE)
+```
+
+The held-out likelihood is highest between 60 and 80, and the residuals are lowest around 50,
+
+```{r}
+library(quanteda)
+library(stm)
+
+talk_dfm <- tidy_talk %>%
+  count(name, word, sort = TRUE) %>%
+  cast_dfm(name, word, n)
+
+# library(slam)
+# talk_dfm_stm <- convert(talk_dfm, to = "stm")
+
+# very time consuming
+# k_search_output <- 
+# searchK(talk_dfm_stm$documents, 
+#         talk_dfm_stm$vocab,
+#         K = seq(10, 100, 20),
+#         cores = 1)
+# 
+# plot(k_search_output)
+
+# takes a few minutes
+topic_model <- stm(talk_dfm, K = 60, 
+                   verbose = FALSE, 
+                   init.type = "Spectral")
+
+plot(topic_model,  text.cex = 0.75)
+
+td_beta <- tidy(topic_model)
+
+library(drlib) # devtools::install_github("dgrtwo/drlib")
+
+td_beta %>%
+    group_by(topic) %>%
+    top_n(10, beta) %>%
+    ungroup() %>%
+    mutate(topic = paste0("Topic ", topic),
+           term = reorder_within(term, beta, topic)) %>%
+    ggplot(aes(term, beta, fill = as.factor(topic))) +
+    geom_col(alpha = 0.8, show.legend = FALSE) +
+    facet_wrap(~ topic, scales = "free_y") +
+    coord_flip() +
+    scale_x_reordered() +
+    theme_minimal(base_size = 6) +
+    labs(x = NULL, y = expression(beta),
+         title = "Highest word probabilities for each topic",
+         subtitle = "Different words are associated with different topics")
+
+ggsave("figures/wh_wikpedia_pages_talk_page_topics.png")
+```
+
+The probability that each document is generated from each topic.
+
+```{r}
+td_gamma <- tidy(topic_model, matrix = "gamma",                    
+                 document_names = rownames(talk_dfm))
+
+ggplot(td_gamma, aes(gamma, fill = as.factor(topic))) +
+  geom_histogram(alpha = 0.8, show.legend = FALSE) +
+  facet_wrap(~ topic, ncol = 3) +
+  labs(title = "Distribution of document probabilities for each topic",
+       y = "Number of stories", x = expression(gamma)) +
+      theme_minimal(base_size = 6)
+
+```
+
+we may want to know which topics are associated with each talk page?
+
+```{r}
+topic_model_gamma <- tidy(topic_model, matrix = "gamma")
+
+topic_model_gamma %>%
+  filter(document %in% 1:10) %>% 
+  mutate(title = reorder(document, gamma * topic)) %>%
+  ggplot(aes(factor(topic), gamma)) +
+  geom_boxplot() +
+  facet_wrap(~ title)
+```
+
+Topic correlations
+
+```{r}
+mod.out.corr <- topicCorr(topic_model)
+
+topic_labels <- labelTopics(topic_model)
+
+topic_tag <- NULL
+for(i in 1:nrow(topic_labels$score)){
+  topic_tag[[i]] <-  paste0(as_tibble(topic_labels$score)[i, 1:3], collapse = "\n")
+}
+
+library(igraph)
+g <- graph.adjacency(mod.out.corr$posadj)
+V(g)$Degree <- degree(g, mode = 'in') # CALCULATE DEGREE
+V(g)$Name <- topic_tag # ADD NAMES
+E(g)$weight <- edge.betweenness(g)
+
+library(ggraph)
+
+ggraph(g, layout = "lgl") + 
+  geom_edge_link0(aes(width = weight), alpha = 0.1) +
+  geom_edge_diagonal(label_colour = "blue", alpha = 0.1) +
+    geom_node_point(aes(size = Degree), alpha = 0.6, colour = "steelblue") + 
+    geom_node_text(aes(label = Name), size = 3) +
+    theme_graph(foreground = 'steelblue', fg_text_colour = 'white')
+
+ggsave("figures/wh_talk_page_topic_correlation_network.png")
 ```

### 2019-05-12 code/paper.Rmd
chord fig looking ok

@@
 
+png(filename = "figures/wh_talk_pages_top_topics.png", width = 1800, height = 2600, res = 300)
+par(bty="n",col="grey40",lwd=10)
 plot(topic_model,  text.cex = 0.75)
+dev.off()
 
@@
 circos.clear()
+png("figures/chord_fig.png", res = 300, width = 2500, height = 2500)
 chordDiagram(adjacency_list, 
@@
 
-```
-
-```{r}
+dev.off()
+
+```
+
+```{r eval=FALSE}
 
@@
 Look at distributions of variables, then say 2sd is extreme, and match those to the WH pages to find out what they are
-
-```{r}
-```
 
@@
 
-for WH sites
+for WH sites, look for editing anomalies using all editors, put a line on for inscpription year so we can see if there are peaks in activity around inscription.
 
@@
 
-n1 <- 7  # edits per month
-n2 <- 20 # months worth of edits
+n1 <- 10  # edits per month
+n2 <- 12 # months worth of edits
 revision_history_page_details_ip_addresses_df_monthly_edits_10 <- 
@@
   filter(n() >= n2) 
-
-```
+```
+
+Anomalies in editing activity
 
@@
   group_by(Site) %>% 
-  filter(max(anoms) >= 10) # where the anomaly is n edits/month or more
+  filter(max(anoms) >= 50) # where the anomaly is n edits/month or more
 
@@
   scale_x_datetime(date_labels="%b\n%Y") +
-  facet_wrap( ~ Site, scales = "free")
+  facet_wrap( ~ Site, scales = "free") +
+  theme_minimal()
 ```

### 2019-05-13 code/paper.Rmd
time series and inscription years

@@
 
-Load the data
+## Load the data
 
@@
 
-## Some sort of clustering
+## Overall clusters
 
@@
 
+## More maps
+
 ```{r}
@@
 
-Here's a map of countries showing which has the most WP pages for WH sites
+## Here's a map of countries showing which has the most WP pages for WH sites
 
@@
 
-Map of the ratio of WH sites with WP pages, per country
+## Map of the ratio of WH sites with WP pages, per country
 
@@
 ```
+
+# basic qualities scatterplot
 
@@
 
-Scatterplot showing the WP sites that get the most attention
+## Scatterplot showing the WP sites that get the most attention
 
@@
 
-Edits per 1k words, as a measure of edit density
+## Edits per 1k words, as a measure of edit density
 
@@
 
-Number of unique editors per page
+## Number of unique editors per page
 
@@
 
-Number of unique editors per 1k words per page
+## Number of unique editors per 1k words per page
 
@@
 
-Size of edits, absolute and raw
+## Size of edits, absolute and raw
 
@@
 
-How many edits made by bots? Proportion of edits per page made by bots
+## How many edits made by bots? Proportion of edits per page made by bots
 
@@
 
-Which WH pages are most edited by bots?
+## Which WH pages are most edited by bots?
 
@@
 
-which bots are most active on WH pages vs random pages?
+## which bots are most active on WH pages vs random pages?
 Cydebot: category edits
@@
 
-So about vandalism? do WH sites get more than random ones?
+## So about vandalism? do WH sites get more than random ones?
 
@@
 
-Which WH pages have the most vandalism?
+## Which WH pages have the most vandalism?
 
@@
 
-Reverts
+## Reverts
 
@@
 
-Which articles have the most reverts?
+## Which articles have the most reverts?
 
@@
 
-Is there a correlation between reverts and vandalism?
+## Is there a correlation between reverts and vandalism?
 
@@
 
-What's the typical distribution of talk page length?
+## What's the typical distribution of talk page length?
 
@@
 
-which WH pages have the longest talk pages?
+## which WH pages have the longest talk pages?
 
@@
 
-Talk page topic modelling
+## Talk page topic modelling
 
@@
 
-The probability that each document is generated from each topic.
+## The probability that each document is generated from each topic.
 
@@
 
-we may want to know which topics are associated with each talk page?
+## we may want to know which topics are associated with each talk page?
 
@@
 
-Topic correlations
+## Topic correlations
 
@@
 
-IP addresses
+## IP addresses
 
@@
 
-How many IP edits on each page?
+## How many IP edits on each page?
 
@@
 
-Overall location of IP edits for all random pages
+## Overall location of IP edits for all random pages
 
@@
 
-What's the geographic diversity of edits per random page?
+## What's the geographic diversity of edits per random page?
 
@@
 
+## Circular chord plot
+
 ```{r}
@@
 
-```{r}
-library(tidytext)
-
-```
-
 What's the typical distribution of the proportion of edits that are reverts?
@@
 
-time between edits
+## time between edits
 
@@
 
-Page ages: are WH pages younger than the typical WP page? What's their relationship to their inscription year?
+## Page ages: are WH pages younger than the typical WP page? What's their relationship to their inscription year?
 
@@
   ggplot() +
-geom_density(aes(as.numeric(edit_span), 
+geom_density(aes(as.numeric(edit_span / 365), 
                  fill = source),
                  alpha = 0.3) +
-  # scale_x_log10() +
+  geom_vline(xintercept = year(Sys.Date()) - 2001, 
+             colour = "red") +
+  annotate("text", x = 15, y = 0.2, label = "start of Wikipedia → ") +
   scale_fill_viridis_d() +  
   theme_minimal(base_size = 12) + 
-  xlab("Age of Wikipedia page (days)")
+  xlab("Age of Wikipedia page (years)")
 
 ggsave("figures/wh_wikpedia_pages_ages.png")
-
-```
-
-Time between inscription year and first edit
+```
+
+## Time between inscription year and first edit
 
@@
 
-time series of edits: breakouts relating to events? monthly seems like a good level of aggregation. What can we do for spike detection?
-
-```{r}
-randoms_revision_history_page_details_ip_location %>% 
-  group_by(page) %>% 
+`all_the_data_to_load_quickly.RData` is up to here
+
+```{r}
+load("data/all_the_data_to_load_quickly.RData")
+
+# remove some big items
+rm(list = ls(pattern = "random"))
+library(tidyverse)
+library(lubridate)
+```
+
+## time series of edits: breakouts relating to events? monthly seems like a good level of aggregation. What can we do for spike detection?
+
+```{r}
+wh_pages_edit_time_series <- 
+wh_pages_talk_page_length %>% 
+  unnest(revision_history_page_details) %>% 
+  filter(Year_num >= 2001) %>% # only sites inscribed after WP started
+  group_by(Site) %>% 
   mutate(the_d = floor_date(rh_date, "day")) %>% 
     mutate(the_m = floor_date(rh_date, "month")) %>% 
-  group_by(page, the_m) %>% 
+  group_by(Site, the_m) %>% 
   tally() %>% 
-  filter(n() > 130) %>%   # explore this value
-  ggplot() +
+  filter(n() > 100) %>% # explore this value
+  left_join(wh_pages_talk_page_length) %>% 
+  mutate(vline_year = ifelse(Year_num >= 2001, Year_num, NA)) %>% 
+  mutate(vline_year = ymd_hms(ISOdatetime(vline_year, 1, 1, 1, 0, 0)))
+
+ggplot(wh_pages_edit_time_series) +
+  geom_vline(aes(xintercept = vline_year), colour = "red") +
   geom_line(aes(the_m,
              n)) +
-  facet_wrap( ~ page, scales = "free")
-
-```
-
-Spike detection
+  facet_wrap( ~ str_wrap(Site, 30), scales = "free") +
+  theme_minimal(base_size = 6)
+
+ggsave("figures/wh_wikpedia_pages_edit_time_series.png", h = 9, w = 12)
+```
+
+## Spike detection
 
@@
   tally() %>% 
-  filter(n() > 150) # explore this value
+  filter(n() > 200) # explore this value
 

### 2019-05-13 code/paper.Rmd
thinking about the talk pages

@@
 
+tidy_talk_raw <- 
+enframe(unlist(wh_wiki_talk_pages)) %>% 
+  bind_cols(wh_wiki_table)
+
+write.csv(tidy_talk_raw$value , "data/wh_wiki_talk_page_text.txt")
+
 tidy_talk <- 
-enframe(unlist(wh_wiki_talk_pages)) %>% 
+  tidy_talk_raw %>% 
     mutate(clean_text = str_remove_all(value, "\n|\t")) %>% 
@@
   filter(!str_detect(word, "\\."))
+
+# check which sites have some words
+tidy_talk %>% 
+  filter(word == "unesco") %>% 
+  group_by(Site) %>% 
+  tally(sort = T)
 
@@
 
+# reload data
+
 `all_the_data_to_load_quickly.RData` is up to here

### 2019-06-28 code/paper.Rmd
stash

@@
   xlab("Proportion of all edits that are anonymous")
+
+ggsave("figures/wh_wikipedia_pages_anon_edits_prop.png")
 ```

### 2019-06-28 code/paper.Rmd
try

@@
 ---
+try ten_k_random_wp_pages_revision_history_page_details_summary_tbl
 
